---
title: "KoCo19 Lab"
author: "Mercè Garí"
date: '2020-08-24'
output:
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
#rmarkdown::render("dashboard.Rmd") # to run it

library(flexdashboard)
library(dplyr)
library(ggplot2)
library(tidyr)
library(ggthemes)
library(GGally)

theme_set(theme_tufte(base_family = "Source Sans Pro",
                      base_size = 10))
invisible(Sys.setlocale(category = "LC_ALL", locale = "en_US"))

lab.orig <- read.csv("KoCo19_BaselineLAB.csv")
lab.orig <- lab.orig[,-1]
ind.orig <- read.csv("KoCo19_indcharacteristics.csv")
ind.orig <- ind.orig[,-1]
hh.orig <- read.csv("KoCo19_hhcharacteristics.csv")
hh.orig <- hh.orig[,-1]

lab <- lab.orig %>%
  rename(IgA = IgA_quant, IgG = IgG_quant,
         Roche = R_quant, NT = NT_quant, CPass = CPass_quant,
         NT.bin = NT_Result, CPass.bin = CPass_Result) %>%
  mutate(IgA.bin = ifelse(IgA < 1.1, "Negative", "Positive"),
         IgG.bin = ifelse(IgG < 1.1, "Negative", "Positive"),
         Roche.bin = ifelse(Roche < 1, "Negative", "Positive"),
         IgA.bin = as.factor(IgA.bin),
         IgG.bin = as.factor(IgG.bin),
         Roche.bin = as.factor(Roche.bin),
         NT = factor(as.character(NT), 
                     levels = c("<10", "10", "20", "40", ">80")))

```


Main tests
==================================================================

Row
-----------------------------------------------------------------------

### Violinplots

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>% 
  tidyr::gather(Antibody, Concentration, c(IgA, IgG, Roche)) %>%
  mutate(Test = ifelse(Antibody == "Roche", "Roche", "Euroimmun"),
         Limit = ifelse(Antibody == "Roche", 1, 1.1)) %>%
  ggplot(aes(y = Concentration, x = Antibody)) +
  geom_violin(alpha = 0.20) +
  scale_y_log10() +
  ylab("Concentration") +
  facet_wrap(~Test, scales="free") +
  xlab("") + 
  geom_hline(aes(yintercept = Limit), col = "grey30", lty = 2) + 
  theme_bw()
```


### Density plots

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>% 
  tidyr::gather(Antibody, Concentration, c(IgA, IgG, Roche)) %>%
  mutate(Test = ifelse(Antibody == "Roche", "Roche", "Euroimmun"),
         Limit = ifelse(Antibody == "Roche", 1, 1.1)) %>%
  ggplot(aes(x = Concentration, color = Antibody, fill = Antibody)) +
  geom_density(alpha = 0.20) +
  scale_x_log10() +
  #facet_wrap(~Test, scales="free") +
  xlab("Concentration") + ylab("Density") +
  theme_bw()
```

Row
-----------------------------------------------------------------------

### Scatterplot Euroimmun IgA and IgG

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  mutate(Status = ifelse(IgG.bin == "Positive" & IgA.bin == "Positive", "Both positives", ifelse(IgG.bin == "Negative" & IgA.bin == "Negative", "Both negatives", "Other"))) %>%
  ggplot(aes(x=IgG, y=IgA, color = Status)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  theme_bw() +
  geom_hline(yintercept = 1.1, col ="grey30", lty = 2) +
  geom_vline(xintercept = 1.1, col ="grey30", lty = 2)
```


### Scatterplot Euroimmun (IgG) and Roche

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  mutate(Status = ifelse(IgG.bin == "Positive" & Roche.bin == "Positive", "Both positives", ifelse(IgG.bin == "Negative" & Roche.bin == "Negative", "Both negatives", "Other"))) %>%
  ggplot(aes(x=IgG, y=Roche, color = Status)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() +
  scale_y_log10() +
  theme_bw() +
  geom_hline(yintercept = 1, col ="grey30", lty = 2) +
  geom_vline(xintercept = 1.1, col ="grey30", lty = 2)
```


Confirmatory tests
==================================================================

Row
-----------------------------------------------------------------------

### CPass
```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  ggplot(aes(x=CPass), fill="grey") +
  geom_density(fill="grey") +
  xlab("CPass concentration") + ylab("Density") +
  theme_bw()
```

### Neutralization
```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  filter(!is.na(NT)) %>%
  ggplot(aes(x=NT)) +
  geom_bar(fill="grey") +
  xlab("NT test value") + ylab("Number of tests") +
  theme_bw()

```

Row
-----------------------------------------------------------------------

### Array

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  tidyr::gather(Array, Concentration, 
                c(VC_S1_IgA, VC_S2_IgA, VC_N_IgA,
                  VC_S1_IgM, VC_S2_IgM, VC_N_IgM,
                  VC_S1_IgG, VC_S2_IgG, VC_N_IgG)) %>%
  ggplot(aes(x=Array, y=Concentration)) +
  geom_violin() +
  geom_point(alpha = 0.5) +
  theme_bw() +
  scale_y_log10() +
  geom_hline(yintercept = 70, color = "red", lty = 2) +
    geom_hline(yintercept = 100, color = "blue", lty = 2)
```


Combination (i)
==================================================================

Row
-----------------------------------------------------------------------

### Boxplot Euroimmun-IgG/Roche vs. Neutralization

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  filter(IgG.bin %in% "Positive" | Roche.bin %in% "Positive") %>%
  tidyr::gather(Antibody, Concentration, c(IgG, Roche)) %>%
  mutate(Limits = ifelse(Antibody == "IgG", 1.1, 1)) %>%
  ggplot(aes(y=Concentration, x = CPass.bin)) +
  geom_boxplot(alpha = 0.4) +
  scale_y_log10() +
  geom_hline(aes(yintercept = Limits), color ="grey", lty =2) +
  facet_wrap(~Antibody) +
  xlab("CPass result") +
  theme_bw() 
```

### Boxplot Euroimmun-IgG/Roche vs. CPass

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  filter(IgG.bin %in% "Positive" | Roche.bin %in% "Positive") %>%
  tidyr::gather(Antibody, Concentration, c(IgG, Roche)) %>%
  mutate(Limits = ifelse(Antibody == "IgG", 1.1, 1)) %>%
  ggplot(aes(y=Concentration, x = NT.bin)) +
  geom_boxplot(alpha = 0.4) +
  scale_y_log10() +
  geom_hline(aes(yintercept = Limits), color ="grey", lty =2) +
  facet_wrap(~Antibody) +
  xlab("NT result") +
  theme_bw() 
```


Row
-----------------------------------------------------------------------

### Spaguetti plot IgG and Roche pairs

```{r, fig.width = 6, fig.height = 3, results = FALSE}
lab %>%
  filter(IgG.bin %in% "Positive" | Roche.bin %in% "Positive") %>%
  mutate(Result = ifelse(IgG.bin == "Positive" & Roche.bin == "Positive", "Both positives", "Other")) %>%
  tidyr::gather(Antibody, Concentration, c(IgG, Roche)) %>%
  ggplot(aes(y=Concentration, x=Antibody, group = ind_id,
             color = Result)) +
  geom_point(alpha = 0.4) +
  geom_line(alpha = 0.1) +
  xlab("") +
  geom_hline(yintercept = 1, lty=2, color="grey") +
  geom_hline(yintercept = 1.1, lty=2, color="grey") +
  scale_y_log10() +
  theme_bw() 
```


### Spaguetti plot IgG and Roche pairs with CPass

```{r, fig.width = 6, fig.height = 3, results = FALSE}
lab %>%
  filter(IgG.bin %in% "Positive" | Roche.bin %in% "Positive") %>%
  tidyr::gather(Antibody, Concentration, c(IgG, Roche)) %>%
  ggplot(aes(y=Concentration, x=Antibody, group = ind_id,
             color = CPass.bin)) +
  geom_point(alpha = 0.4) +
  geom_line(alpha = 0.1) +
  xlab("") +
  geom_hline(yintercept = 1, lty=2, color="grey") +
  geom_hline(yintercept = 1.1, lty=2, color="grey") +
  scale_y_log10() +
  theme_bw() 
```


### Spaguetti plot IgG and Roche pairs with NT

```{r, fig.width = 6, fig.height = 3, results = FALSE}
lab %>%
  filter(IgG.bin %in% "Positive" | Roche.bin %in% "Positive") %>%
  tidyr::gather(Antibody, Concentration, c(IgG, Roche)) %>%
  ggplot(aes(y=Concentration, x=Antibody, group = ind_id,
             color = NT.bin)) +
  geom_point(alpha = 0.4) +
  geom_line(alpha = 0.1) +
  xlab("") +
  geom_hline(yintercept = 1, lty=2, color="grey") +
  geom_hline(yintercept = 1.1, lty=2, color="grey") +
  scale_y_log10() +
  theme_bw() 
```


Combination (ii)
==================================================================

Row
-----------------------------------------------------------------------

### Scatterplot Roche/IgG vs CPass/NT results

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  #filter(IgG.bin %in% "Positive" | Roche.bin %in% "Positive") %>%
  mutate(Result = ifelse(IgG.bin == "Positive" & Roche.bin == "Positive", "Both positives", "Other")) %>%
  tidyr::gather(Test, Result, c(CPass.bin, NT.bin)) %>%
  ggplot(aes(y=IgG, x = Roche, color = Result)) +
  geom_point() +
  scale_y_log10() + scale_x_log10() +
  facet_grid(~Test) +
  geom_vline(xintercept = 1, color ="grey", lty=2) +
  geom_hline(yintercept = 1.1, color="grey", lty=2) +
  theme_bw() 
```


Combination (iii)
==================================================================

Row
-----------------------------------------------------------------------


### Scatterplot Roche/IgG vs Array (threshold 70)

```{r, fig.width = 8, fig.height = 3, results = FALSE}
# For array, threshold of 70
lab %>%
  tidyr::gather(Test, Result, 
                c(CPass.bin, NT.bin, 
                  VC_S1_IgA_Result_c70, VC_S2_IgA_Result_c70, 
                  VC_N_IgA_Result_c70, VC_S1_IgM_Result_c70, 
                  VC_S2_IgM_Result_c70, VC_N_IgM_Result_c70, 
                  VC_S1_IgG_Result_c70, VC_S2_IgG_Result_c70, 
                  VC_N_IgG_Result_c70)) %>%
  ggplot(aes(y=IgG, x = Roche, color = Result)) +
  geom_point(alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  facet_wrap(~Test) +
  geom_vline(xintercept = 1, color ="grey", lty=2) +
  geom_hline(yintercept = 1.1, color="grey", lty=2) +
  theme_bw() 
```


Combination (iv)
==================================================================

Row
-----------------------------------------------------------------------


### Pairs (to be finished)

```{r, fig.width = 8, fig.height = 3, results = FALSE}
lab %>%
  filter(!is.na(NT)) %>%
  select(IgA, IgG, Roche, CPass, NT) %>%
  ggpairs() +
  theme_bw()

```


PCR results
==================================================================

Row
-----------------------------------------------------------------------

### Previous PCR test and main tests

```{r, fig.width = 8, fig.height = 3, results = FALSE}
# How many of the initially sero-positive individuals in the baseline-study were previously tested by pharyngeal swab and nucleic acid amplification (PCR) (positively or negatively) and/or had symptoms suggestive for COVID-19 (yes or no)?

lab %>%
  pivot_longer(c("IgG", "IgA", "Roche"), 
               names_to = "Antibody", 
               values_to = "Concentration") %>%
  left_join(select(ind.orig, ind_id, Testing_positive)) %>%
  mutate(`Previous PCR Test` = Testing_positive) %>%
  ggplot(aes(x=`Previous PCR Test`, y=Concentration)) +
  geom_boxplot(alpha=0.5) +
  scale_x_discrete(labels = c("Negative", "Result not\navailable yet", "Positive")) +
  facet_wrap(~Antibody) +
  ylab("Antibody concentration") +
  geom_hline(yintercept = 1.1, col = "grey30", lty = 2) + 
  theme_bw() +
  scale_y_log10()


```



About
==================================================================

These plots are only based on KoCo19 data.

