---
title: "Lab Paper 2nd part"
author: "Mercè Garí"
output:
  html_document:
    df_print: paged
    dev: png
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

Compilation date: `r format(Sys.time(), '%d.%m.%Y')`

# Prepare

```{r}
here_r = function (...) here::here("Statistics", "R", ...)
here_lab_data = function (...) here::here("Lab_paper2_data", ...)
here_out = function (...) here::here(
  "Lab_paper2_output", "lab_figures_merce", ...)

# Create output folder if inexistent
dir.create(here_out(), showWarnings = FALSE)

library(magrittr)
library(ggplot2)
library(grid)

# Load settings
source(here_r("setup.R"))
source(here_r("functions.R"))

library(dplyr)
source(here_r("RainCloudPlots", "R_rainclouds.R"))


# Load data
#  Single data contains only one blood sample per participant
single_data = read.csv(here_lab_data(
  "Global_Data", "Final_Lab_Single_20200904.csv"), stringsAsFactors = F)

# Assertions
if (length(unique(single_data$blut_ID)) != nrow(single_data)) {stop("Blood id not unique")}
if (length(unique(single_data$tln_ID)) != nrow(single_data)) {stop("Participant id not unique")}

###############################################################################
# Clean data

data = single_data

#  Unique labels
data[data=="Positiv" | data=="pos." | data=="reactive" | 
       data=="positive"] = "Positive"
data[data=="Negativ" | data=="Indeterminate" | 
       data=="neg." | data=="ind." | 
       data=="nonreactive" | data=="negative" | 
       data=="not_reactive"] = "Negative"

#  Remove Roche 0 values
val_cols = grep("roche_COI", colnames(data), value=T)
res_cols = grep("roche_Interpretation", colnames(data), value=T)
cat("# Roche == 0 before removal:", sum(data[,val_cols]==0, na.rm=T), "\n")

for (j in 1:length(val_cols)) {
  # Conveniently, the order is the same
  val_col = val_cols[[j]]
  res_col = res_cols[[j]]
  data[data[,val_col]==0 & !is.na(data[,val_col]), res_col] = NA
  data[data[,val_col]==0 & !is.na(data[,val_col]), val_col] = NA
}

#  Add binary ground truth column
data['Ground truth'] = ifelse(is.na(data$model_outcome), "Unknown", 
                              ifelse(data$model_outcome=="true_positive",
                                     "True-positive",
                                     "True-negative"))
data$`Ground truth` = factor(as.character(data$`Ground truth`),
                             levels = c("Unknown", "True-negative", 
                                        "True-positive"))

#  NT to categories with correct ordering
data$NT = factor(as.character(data$NT), 
                 levels = c("<10", "10", "20", "40", ">80"))

# TODO currently is 4.75, which is bad when setting manually <10 -> 5
cutoff$new$NT = 10

###############################################################################
# Check data consistency

#' Check consistency of reported values according to assumed thresholds
check_consistency = function(val_cols, res_cols, threshold) {
  for (j in 1:length(val_cols)) {
    # Assuming that value and result columns have the same order
    val_col = val_cols[[j]]
    res_col = res_cols[[j]]
    by_value = sum(data[,val_col]>=threshold, na.rm=T)
    by_cat = sum(data[,res_col] == "Positive", na.rm=T)
    if (by_value != by_cat) { stop(paste("Mismatch positives (exp./act.)", by_value, by_cat)) }
    by_value = sum(data[,val_col]<threshold, na.rm=T)
    by_cat = sum(data[,res_col] == "Negative", na.rm=T)
    if (by_value != by_cat) { stop(paste("Mismatch negatives (exp./act.)", by_value, by_cat)) }
  }
}

#  Roche
val_cols = grep("roche_COI", colnames(data), value=T)
res_cols = grep("roche_Interpretation", colnames(data), value=T)
check_consistency(val_cols, res_cols, 1.0)
if (any(data[,val_cols]==0, na.rm=T)) {stop("There are Roche zero values.")}

#  Euroimmun
val_cols = grep("eur_quotient", colnames(data), value=T)
res_cols = grep("eur_der_test_result", colnames(data), value=T)
check_consistency(val_cols, res_cols, 1.1)
if (any(data[,val_cols]==0, na.rm=T)) {stop("There are Euroimmun zero values.")}

# Use corrected data frame
single_data = data

# Tidy up
rm(data, val_cols, res_cols, val_col, res_col, j)

#' Create a plot with the `title` string above the `plt` plot row.
title_plot = function(title, plt, plot.margin=margin(0,0,0,7), rel_heights=c(0.1,1)) {
  plot_grid(
    ggdraw() + draw_label(title, fontface='bold', x=0, hjust=0) + theme(plot.margin = plot.margin),
    plt, ncol=1, rel_heights=rel_heights
  )
}

```

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggpmisc)
library(stringr)
library(GGally)
library(cowplot)
library(forcats)

lab <- extract_last_values(single_data) %>%
  as_tibble() %>%
  rename(IgA = Eur_IgA, IgG = Eur_IgG,
         cPass = cPass,
         NT.bin = NT_result, cPass.bin = cPass_result,
         Cohort = study_per_ID) %>%
  mutate(IgA.bin = ifelse(IgA < 1.1, "Negative", "Positive"),
         IgG.bin = ifelse(IgG < 1.1, "Negative", "Positive"),
         Roche.bin = ifelse(Roche < 1, "Negative", "Positive"),
         IgA.bin = as.factor(IgA.bin),
         IgG.bin = as.factor(IgG.bin),
         Roche.bin = as.factor(Roche.bin),
         NT = factor(as.character(NT), 
                     levels = c("<10", "10", "20", "40", ">80"))) %>%
  rename(`Previous PCR Test` = PCR_Ergebnis)

lab.array <- lab %>%
  select(tln_ID, blut_ID, 
         VC_S1_IgA, VC_S2_IgA, VC_N_IgA,
         VC_S1_IgG, VC_S2_IgG, VC_N_IgG,
         VC_S1_IgM, VC_S2_IgM, VC_N_IgM) %>%
  gather(array, value, -c(tln_ID, blut_ID)) %>%
    mutate(value = ifelse(value == "<10", "5", value),
           value = as.numeric(value)) %>%
  spread(array, value)

lab <- lab %>%
  select(-c(VC_S1_IgA, VC_S2_IgA, VC_N_IgA,
         VC_S1_IgG, VC_S2_IgG, VC_N_IgG,
         VC_S1_IgM, VC_S2_IgM, VC_N_IgM)) %>%
  left_join(lab.array)


lab.lineblot <- lab %>%
  select(tln_ID, blut_ID,
         LineBlot_NP_SARS_2, LineBlot_RBD_SARS_2,
         LineBlot_S1_SARS_2, 
         Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1) %>%
  gather(lineblot, value, -c(tln_ID, blut_ID)) %>%
  mutate(value = ifelse(value == "Negative", "0.5", value),
         value = as.numeric(value)) %>%
  spread(lineblot, value)

lab <- lab %>%
  select(-c(LineBlot_NP_SARS_2, LineBlot_RBD_SARS_2,
         LineBlot_S1_SARS_2,
         Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  left_join(lab.lineblot)


# Thresholds
thr.man <- as.data.frame(cutoff$old) %>%
  gather(Test, Manufacturer)
thr.cal <- as.data.frame(cutoff$new) %>%
  gather(Test, Optimized)
thresholds <- left_join(thr.man, thr.cal) %>%
  mutate(Test = ifelse(Test == "Eur_IgA", "IgA",
                       ifelse(Test == "Eur_IgG", "IgG", Test))) %>%
  as_tibble()
thresholds <- as.data.frame(thresholds)
# Add manually the Common cold thresholds (1 for all)
thresholds.additional <- data.frame(Test = c("Schnupfen_NP_229E",
                                             "Schnupfen_NP_NL63",
                                             "Schnupfen_NP_OC43",
                                             "Schnupfen_NP_HKU1"),
                                    Manufacturer = rep(1, 4),
                                    Optimized = rep(1, 4))
                                      
thresholds <- rbind(thresholds, thresholds.additional)
thresholds$Manufacturer[thresholds$Test == "NT"] <- 10
str(thresholds)

lab.long <- lab %>%
  tidyr::gather(Test, value, 
                c(Roche, IgG, IgA, NT, cPass, 
                  VC_S1_IgA, VC_S2_IgA,  
                  VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, 
                  VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  select(tln_ID, blut_ID, Test, value, `Ground truth`) 

lab.long.wo <- lab %>%
  tidyr::gather(Test, value, 
                c(Roche, IgG, IgA, cPass, 
                  VC_S1_IgA, VC_S2_IgA,  
                  VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, 
                  VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  select(tln_ID, blut_ID, Test, value, `Ground truth`) 
  
Test.names <- data.frame(Test = unique(lab.long$Test),
                         name = c("Ro-N-Ig", "EI-S1-IgG", "EI-S1-IgA",
                                  "NT", "GS-cPass", 
                                  "VC S1 IgA", "VC S2 IgA", "VC N IgA",
                                  "VC S1 IgM", "VC S2 IgM", "VC N IgM",
                                  "VC S1 IgG", "VC S2 IgG", "VC N IgG",
                                  "MG-N", "MG-RBD", "MG-S1", 
                                  "NP-229E", "NP NL63", "NP-OC43", "NP-HKU1"))

Test.names
```


### Plots for Figure 4A


```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

# IgA vs IgG

# for IgA in x-axis
v <- 3
#for(v in 1:length(unique(lab.long$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))
 
 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plots

 # IgA vs. IgG

iga.igg <- lab.long.wo %>% filter(Test %in% c("IgA", "IgG")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` == "True-negative"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` == "True-positive"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.15,0.15))) + 
  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "IgG"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "IgG"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("EI-S1-IgG") + xlab("EI-S1-IgA") +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.30, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.2, vjust=2.30, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=-0.3, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.4, show.legend=FALSE, size=3.5) +
       geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.3, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.4, show.legend=FALSE, size=3.5) +
   ggpubr::stat_cor(aes(color=`Ground truth`,
                       hjust=0, vjust=0),
                       p.accuracy=0.001, r.accuracy=0.01,
                   label.x.npc=0.1, label.y.npc = 1,
                   show.legend=FALSE, size=3) +
  theme(legend.position="none")
  
iga.igg
 


# Roche vs IgG

# for Roche in x-axis
v <- 1
#for(v in 1:length(unique(lab.long$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))
 
 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plots
 
# Correct the percentage of true positives manually (to sum up 100)
 counts.now <- counts.now %>%
   mutate(Percentage = ifelse(Test == "IgG" & 
                                `Ground truth` == "True-positive" &
                                quadrant == 3, 12, Percentage))
 # Roche vs. IgG

roche.igg <- lab.long.wo %>% filter(Test %in% c("Roche", "IgG")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` == "True-negative"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` == "True-positive"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.15,0.15))) + 
  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "IgG"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "IgG"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("EI-S1-IgG") + xlab("Ro-N-Ig") +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.30, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.30, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=-0.3, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.4, show.legend=FALSE, size=3.5) +
       geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-positive" & 
                            Test == "IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.3, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-negative" & 
                            Test == "IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.4, show.legend=FALSE, size=3.5) +
  ggpubr::stat_cor(aes(color=`Ground truth`,
                       hjust=0, vjust=0),
                       p.accuracy=0.001, r.accuracy=0.01,
                   label.x.npc=0.7, label.y.npc = 0.1,
                   show.legend=FALSE, size=3)
roche.igg

legend <- cowplot::get_legend(roche.igg)
legend
grid.newpage()
grid.draw(legend)
roche.igg <- roche.igg + theme(legend.position="none")

# Save the plot data, as this is required as input in `lab_figures_yannik.Rmd`
save(iga.igg, roche.igg, legend, file=here_r("Lab-Fig-6-Part-A.RData"))

#plot_grid(iga.igg, roche.igg, legend, labels=c("A", "", ""), nrow=1)
#ggsave(here_out("lab-fig4a-201006.pdf"), width=10, height=5)
#ggsave(here_out("lab-fig4a-201006.png"), width=10, height=5)
```



### Plots for Figure 6


```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

# For A) NT vs cPass
no.se.que <- lab %>%
  select(tln_ID, blut_ID, NT, cPass, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, NT)) %>%
  left_join(thresholds) %>%
  mutate(quadrant = case_when(
    value < Optimized & NT == "<10" ~ "<10-below",
    value >= Optimized & NT == "<10" ~ "<10-above",
    value < Optimized & NT == "10" ~ "10-below",
    value >= Optimized & NT == "10" ~ "10-above",
    value < Optimized & NT == "20" ~ "20-below",
    value >= Optimized & NT == "20" ~ "20-above",
    value < Optimized & NT == "40" ~ "40-below",
    value >= Optimized & NT == "40" ~ "40-above",
    value < Optimized & NT == ">80" ~ ">80-below",
    value >= Optimized & NT == ">80" ~ ">80-above")) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant)) 
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n()) 
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100)
counts 
# For the column-wise n
cwn <- counts.quadrant %>%
  mutate(category = gsub("-.+", "", quadrant)) %>%
  group_by(category) %>%
  summarize(n.total = sum(n))
cwn


p1 <- lab %>%
  filter(!is.na(NT)) %>%
  mutate(NT = factor(as.character(NT), 
                      levels = c("<10", "10", "20", "40", ">80"))) %>%
  ggplot(aes(y=cPass, x=NT, color=`Ground truth`)) +
  # Violin plots on the right
  #   geom_flat_violin(aes(fill=`Ground truth`, color= `Ground truth`),
  #                    position = position_nudge(x=.02, y=0),
  #                   alpha=0.3, trim=F, scale="area") +
   geom_flat_violin(data = .%>% filter(`Ground truth` == "Unknown"),
                   fill=style$col_grey, col=style$col_grey,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
                   fill=style$col_truepos, col=style$col_truepos,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
                   fill=style$col_trueneg, col=style$col_trueneg,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  # Jitter points on the left
  geom_point(aes(x=as.numeric(NT)-0.25, y=cPass,
                 col=`Ground truth`),
             position = position_jitter(width = .17, ), alpha=0.5) +
  scale_color_manual(values=style$pal3) +
  geom_hline(data = filter(thresholds, Test == "cPass"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "cPass"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept=1.5, color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new))  +
  theme(legend.position="none") +
  geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.15, y=-50, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-negative"),
            aes(x=1.15, y=-50, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.15, y=130, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "10-below" & 
                            `Ground truth` == "True-positive"),
            aes(x=2.15, y=-50, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=2.15, y=130, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "20-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=3.15, y=130, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "40-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=4.15, y=130, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5)  +
  geom_text(data = filter(counts, quadrant == ">80-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=5.15, y=130, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  annotate("text", x=c(1:5), y=140, size=3,
           label=c(paste("n=", cwn$n.total))) +
  ylab("GS-cPass")

p1

# For B) NT vs LineBlot RBD
no.se.que <- lab %>%
  select(tln_ID, blut_ID, NT, LineBlot_RBD_SARS_2, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, NT)) %>%
  left_join(thresholds) %>%
  mutate(quadrant = case_when(
    value < Optimized & NT == "<10" ~ "<10-below",
    value >= Optimized & NT == "<10" ~ "<10-above",
    value < Optimized & NT == "10" ~ "10-below",
    value >= Optimized & NT == "10" ~ "10-above",
    value < Optimized & NT == "20" ~ "20-below",
    value >= Optimized & NT == "20" ~ "20-above",
    value < Optimized & NT == "40" ~ "40-below",
    value >= Optimized & NT == "40" ~ "40-above",
    value < Optimized & NT == ">80" ~ ">80-below",
    value >= Optimized & NT == ">80" ~ ">80-above")) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant)) 
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n()) 
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100)
counts 
# For the column-wise n
cwn <- counts.quadrant %>%
  mutate(category = gsub("-.+", "", quadrant)) %>%
  group_by(category) %>%
  summarize(n.total = sum(n))
cwn

p2 <- lab %>%
  filter(!is.na(NT)) %>%
  mutate(NT = factor(as.character(NT), 
                      levels = c("<10", "10", "20", "40", ">80"))) %>%
  ggplot(aes(y=LineBlot_RBD_SARS_2, x=NT, color=`Ground truth`)) +
  # Violin plots on the right
  geom_flat_violin(data = .%>% filter(`Ground truth` == "Unknown"),
                   fill=style$col_grey, col=style$col_grey, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
                   fill=style$col_truepos, col=style$col_truepos, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
                   fill=style$col_trueneg, col=style$col_trueneg, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") + 
  # Jitter points on the left
  geom_point(aes(x=as.numeric(NT)-0.25, y=LineBlot_RBD_SARS_2,
                 col=`Ground truth`),
             position = position_jitter(width = .17, ), alpha=0.5) +
  scale_color_manual(values=style$pal3) +
  geom_hline(data = filter(thresholds, Test == "LineBlot_RBD_SARS_2"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "LineBlot_RBD_SARS_2"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
   geom_vline(xintercept=1.5, color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("Line Blot RBD") +
  scale_y_log10(breaks=c(0.5, 1, 3, 10), labels=c("<1", "1", "3", "10")) +
  theme(legend.position="none") +
  geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.15, y=0.15, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-negative"),
            aes(x=1.15, y=0.15, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.15, y=25, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "10-below" & 
                            `Ground truth` == "True-positive"),
            aes(x=2.15, y=0.15, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=2.15, y=25, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "20-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=3.15, y=25, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "40-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=4.15, y=25, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5)  +
  geom_text(data = filter(counts, quadrant == ">80-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=5.15, y=25, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
   annotate("text", x=c(1:5), y=35, size=3,
           label=c(paste("n=", cwn$n.total))) +
  ylab("MG-RBD")
p2

# For C) cPass vs LineBlot RBD
full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(lab.long$`Ground truth`))

no.se.que <- lab %>%
  select(tln_ID, blut_ID, cPass, LineBlot_RBD_SARS_2, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`)) %>%
  left_join(thresholds) %>%
  mutate(Position = ifelse(value < Optimized, "Below", "Above")) %>%
  select(-value, -Manufacturer, -Optimized) %>%
  spread(Test, Position) %>%
  mutate(quadrant = case_when(
    cPass == "Above" & LineBlot_RBD_SARS_2 == "Above" ~ 1,
    cPass == "Below" & LineBlot_RBD_SARS_2 == "Above" ~ 2,
    cPass == "Below" & LineBlot_RBD_SARS_2 == "Below" ~ 3,
    cPass == "Above" & LineBlot_RBD_SARS_2 == "Below" ~ 4)) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant)) 
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n()) 
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100) %>%
  full_join(full.quadrants) %>%
  mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
counts 

p3 <- ggplot(lab, aes(y=LineBlot_RBD_SARS_2, x=cPass, color=`Ground truth`)) +
  geom_point(alpha=0.5) +
  scale_color_manual(values=style$pal3) +
#  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) + 
  scale_y_log10(limits=c(0.45, 15), 
                breaks=c(0.5, 1, 3, 10), labels=c("<1", 1, 3, 10),
                expand=expansion(mult=c(0.1, 0.1))) +
  ylab("Line Blot RBD") +
  geom_hline(data = filter(thresholds, Test == "LineBlot_RBD_SARS_2"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "LineBlot_RBD_SARS_2"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept=thresholds$Manufacturer[thresholds$Test == "cPass"], 
             lty=style$thr_lt_old, color=style$thr_lc_old) +
  geom_vline(xintercept=thresholds$Optimized[thresholds$Test == "cPass"],
             lty=style$thr_lt_new, color=style$thr_lc_new)  +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  geom_text(data = filter(counts, quadrant == 1 & 
                            `Ground truth` == "True-positive"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 1 & 
                            `Ground truth` == "True-negative"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.30, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 2 & 
                            `Ground truth` == "True-positive"),
            aes(x=-Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 2 & 
                            `Ground truth` == "True-negative"),
            aes(x=-Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.30, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 3 & 
                            `Ground truth` == "True-positive"),
            aes(x=-Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-0.3, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 3 & 
                            `Ground truth` == "True-negative"),
            aes(x=-Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=0, vjust=-1.4, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 4 & 
                            `Ground truth` == "True-positive"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.3, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == 4 & 
                            `Ground truth` == "True-negative"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.4, show.legend=FALSE, size=3.5) +
  xlab("GS-cPass") + ylab("MG-RBD")

p3  

library(grid)
library(gridExtra)
legend <- cowplot::get_legend(p3)
legend
grid.newpage()
grid.draw(legend)
p3 <- p3 + theme(legend.position="none")

p3



# Spaguetti plots (parallel coordinates) for NT, cPass and RBD
p4 <- lab %>%
  select(tln_ID, blut_ID, `Ground truth`, NT, cPass, LineBlot_RBD_SARS_2) %>%
  mutate(NT = as.character(NT),
         NT = ifelse(NT == "<10", "-30", ifelse(NT == ">80", "80", NT))) %>%
  mutate(LineBlot_RBD_SARS_2 = ifelse(LineBlot_RBD_SARS_2 == 0.5, -4, LineBlot_RBD_SARS_2)) %>%
  rename(`GS-cPass` = cPass,
         `MG-RBD` = LineBlot_RBD_SARS_2) %>%
  mutate(`MG-RBD` = `MG-RBD` * 7.5) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`)) %>%
  mutate(value = as.numeric(value)) %>%
  ggplot(aes(x=Test, y=value, color=`Ground truth`, group=tln_ID)) +
  geom_point(alpha=0.5) +
  geom_line(alpha=0.5) +
  scale_color_manual(values=style$pal3) +
 # scale_y_log10() +
  #scale_y_log10(limits=c(-75, 100),
   #             breaks=c(1, 10, 20, 40, 80), labels=c("<1", "<10", 20, 40, ">80")) +
  xlab("") + ylab("Measurement value") +
  theme(legend.position="none") +
  scale_y_continuous("Measurement value (GS-cPass)", 
                breaks=c(1, 20, 50, 100),
                labels=c(1, 20, 50, 100),
                sec.axis=sec_axis(~./7.5, 
                name="Measurement value (MG-RBD)",
                breaks=c(-4, 1, 5, 10, 13),
                labels=c("<1", 1, 5, 10, 13))) +
  #geom_vline(xintercept=3.15) +
  annotate("text", x=3.175, y=c(-30.2, 10.1, 20.1, 40.1, 80.1), label=c("<10", "10", "20", "40", ">80"),
           size=3, fontface="plain")
p4  




plot_grid(
  plot_grid(
    title_plot("A", plot_grid(p1)),
    title_plot("B", p2),
    nrow=1, rel_widths = c(1,1)),
  plot_grid(
    title_plot("C", p3),
    title_plot("D", p4), 
    legend,
    nrow=1, rel_widths = c(0.35,0.45, 0.2)),
  nrow=2)

#ggsave("lab-fig6-201027.pdf", width=10, height=8)
#ggsave("lab-fig6-201027.png", width=10, height=8)
ggsave(here_out("Lab-Figure6.png"), width=10, height=8, units="in")
ggsave(here_out("Lab-Figure6.pdf"), width=10, height=8, units="in")
```



### Plots for Figure 7 (new plots changed axes)


```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}


#----------------------------------------------- Fig7 - A

# For NT vs IgG
no.se.que <- lab %>%
  select(tln_ID, blut_ID, NT, IgG, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, NT)) %>%
  left_join(thresholds) %>%
  mutate(quadrant = case_when(
    value < Optimized & NT == "<10" ~ "<10-below",
    value >= Optimized & NT == "<10" ~ "<10-above",
    value < Optimized & NT == "10" ~ "10-below",
    value >= Optimized & NT == "10" ~ "10-above",
    value < Optimized & NT == "20" ~ "20-below",
    value >= Optimized & NT == "20" ~ "20-above",
    value < Optimized & NT == "40" ~ "40-below",
    value >= Optimized & NT == "40" ~ "40-above",
    value < Optimized & NT == ">80" ~ ">80-below",
    value >= Optimized & NT == ">80" ~ ">80-above")) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant)) 
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n()) 
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100)
counts 
# For the column-wise n
cwn <- counts.quadrant %>%
  mutate(category = gsub("-.+", "", quadrant)) %>%
  group_by(category) %>%
  summarize(n.total = sum(n))
cwn
p7a <- lab %>%
  filter(!is.na(NT)) %>%
  mutate(NT = factor(as.character(NT), 
                      levels = c("<10", "10", "20", "40", ">80"))) %>%
  ggplot(aes(y=IgG, x=NT, color=`Ground truth`)) +
  # Violin plots on the right
  geom_flat_violin(data = .%>% filter(`Ground truth` == "Unknown"),
                   fill=style$col_grey, col=style$col_grey, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
                   fill=style$col_truepos, col=style$col_truepos, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
                   fill=style$col_trueneg, col=style$col_trueneg, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  # Jitter points on the left
  geom_point(aes(x=as.numeric(NT)-0.25, y=IgG,
                 col=`Ground truth`),
             position = position_jitter(width = .17, ), alpha=0.5) +
  scale_color_manual(values=style$pal3) +
  geom_hline(data = filter(thresholds, Test == "IgG"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "IgG"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new))  +
  theme(legend.position="none") +
  scale_y_log10() +
  geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-negative"),
            aes(x=1.30, y=0.02, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.30, y=0.02, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.30, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=2.30, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "20-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=3.30, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "40-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=4.30, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5)  +
  geom_text(data = filter(counts, quadrant == ">80-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=5.30, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  annotate("text", x=c(1:5), y=75, size=3,
           label=c(paste("n=", cwn$n.total))) +
  xlab("NT") + ylab("EI-S1-IgG") +
  geom_vline(xintercept=1.5, col=style$thr_lc_new, lty=style$thr_lt_new) +
    geom_vline(xintercept=1.5, col=style$thr_lc_old, lty=style$thr_lt_old)

p7a


#----------------------------------------------- Fig7 - B

# for IgG in y-axis
v <- 2
#for(v in 1:length(unique(lab.long$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Below" & Position.main == "Above" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Above" & Position.main == "Below" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))
 
 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plots
 
# IgG vs. cPass
p7b <- lab.long.wo %>% filter(Test %in% c("IgG", "cPass")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(x = "value", y = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) + 
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_y_log10(expand=expansion(mult=c(0.2, 0.2))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_vline(data = filter(thresholds.now, Test %in%  "cPass"),
             aes(xintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_vline(data = filter(thresholds.now, Test %in% "cPass"),
             aes(xintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_hline(yintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_hline(yintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.3, show.legend=FALSE, size=3.5) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=-Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=-Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.3, show.legend=FALSE, size=3.5) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=-Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.2, vjust=-0.3, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=-Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.4, show.legend=FALSE, size=3.5) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.3, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.4, show.legend=FALSE, size=3.5) +
  theme(legend.position = "none") +
  ylab("EI-S1-IgG") +
  xlab("GS-cPass")
p7b

#----------------------------------------------- Fig7 - C

# IgG vs. LineBlot MG-RBD
p7c <- lab.long.wo %>% filter(Test %in% c("IgG", "LineBlot_RBD_SARS_2")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(x = "value", y = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) + 
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_vline(data = filter(thresholds.now, Test %in%  "LineBlot_RBD_SARS_2"),
             aes(xintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_vline(data = filter(thresholds.now, Test %in% "LineBlot_RBD_SARS_2"),
             aes(xintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_hline(yintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_hline(yintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.2, vjust=-0.3, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.4, show.legend=FALSE, size=3.5) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.3, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.4, show.legend=FALSE, size=3.5) +
  theme(legend.position = "none") +
  ylab("EI-S1-IgG") +
  xlab("MG-RBD") +
  scale_x_log10(breaks=c(0.5,  1, 3, 10), labels=c("<1", "1", "3", "10"))
p7c

#----------------------------------------------- Fig7 - D

# IgG vs. LineBlot MG-N
p7d <- lab.long.wo %>% filter(Test %in% c("IgG", "LineBlot_NP_SARS_2")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(x = "value", y = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) + 
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_vline(data = filter(thresholds.now, Test %in%  "LineBlot_NP_SARS_2"),
             aes(xintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_vline(data = filter(thresholds.now, Test %in% "LineBlot_NP_SARS_2"),
             aes(xintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_hline(yintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_hline(yintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.2, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.15, show.legend=FALSE, size=3.5) +
  theme(legend.position = "none") +
  ylab("EI-S1-IgG") +
  xlab("MG-N") +
  scale_x_log10(breaks=c(0.5,  1, 3, 10), labels=c("<1", "1", "3", "10"))
p7d

#----------------------------------------------- Fig7 - E

# For NT vs Roche
no.se.que <- lab %>%
  select(tln_ID, blut_ID, NT, Roche, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, NT)) %>%
  left_join(thresholds) %>%
  mutate(quadrant = case_when(
    value < Optimized & NT == "<10" ~ "<10-below",
    value >= Optimized & NT == "<10" ~ "<10-above",
    value < Optimized & NT == "10" ~ "10-below",
    value >= Optimized & NT == "10" ~ "10-above",
    value < Optimized & NT == "20" ~ "20-below",
    value >= Optimized & NT == "20" ~ "20-above",
    value < Optimized & NT == "40" ~ "40-below",
    value >= Optimized & NT == "40" ~ "40-above",
    value < Optimized & NT == ">80" ~ ">80-below",
    value >= Optimized & NT == ">80" ~ ">80-above")) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant)) 
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n()) 
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100)
counts 
# For the column-wise n
cwn <- counts.quadrant %>%
  mutate(category = gsub("-.+", "", quadrant)) %>%
  group_by(category) %>%
  summarize(n.total = sum(n))
cwn
p7e <- lab %>%
  filter(!is.na(NT)) %>%
  mutate(NT = factor(as.character(NT), 
                      levels = c("<10", "10", "20", "40", ">80"))) %>%
  ggplot(aes(y=Roche, x=NT, color=`Ground truth`)) +
  # Violin plots on the right
  geom_flat_violin(data = .%>% filter(`Ground truth`== "Unknown"),
                   fill=style$col_grey, col=style$col_grey, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
                   fill=style$col_truepos, col=style$col_truepos, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
                   fill=style$col_trueneg, col=style$col_trueneg, 
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  # Jitter points on the left
  geom_point(aes(x=as.numeric(NT)-0.25, y=Roche,
                 col=`Ground truth`),
             position = position_jitter(width = .17, ), alpha=0.5) +
  scale_color_manual(values=style$pal3) +
  geom_hline(data = filter(thresholds, Test == "Roche"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "Roche"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new))  +
  theme(legend.position="none") +
  geom_text(data = filter(counts, quadrant == "<10-below" & 
                            `Ground truth` == "True-negative"),
            aes(x=1.30, y=0.001, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-above" & 
                            `Ground truth` == "True-negative"),
            aes(x=1.30, y=5000, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts, quadrant == "<10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=1.30, y=5000, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "10-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=2.30, y=5000, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "20-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=3.30, y=5000, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts, quadrant == "40-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=4.30, y=5000, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5)  +
  geom_text(data = filter(counts, quadrant == ">80-above" & 
                            `Ground truth` == "True-positive"),
            aes(x=5.30, y=5000, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
  scale_y_log10(breaks=c(0.05, 1, 10, 100, 1000), 
                labels=c("0.05", "1", "10", "100", "1000")) +
  annotate("text", x=c(1:5), y=20000, size=3,
           label=c(paste("n=", cwn$n.total))) +
  xlab("NT") + ylab("Ro-N-Ig") +
    geom_vline(xintercept=1.5, col=style$thr_lc_new, lty=style$thr_lt_new) +
    geom_vline(xintercept=1.5, col=style$thr_lc_old, lty=style$thr_lt_old)


p7e

#----------------------------------------------- Fig7 - F

# for Roche in y-axis
v <- 1
#for(v in 1:length(unique(lab.long$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Below" & Position.main == "Above" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Above" & Position.main == "Below" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))
 
 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plots
 
# Roche vs. cPass
p7f <- lab.long.wo %>% filter(Test %in% c("Roche", "cPass")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(x = "value", y = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) + 
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_vline(data = filter(thresholds.now, Test %in%  "cPass"),
             aes(xintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_vline(data = filter(thresholds.now, Test %in% "cPass"),
             aes(xintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_hline(yintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_hline(yintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=-Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=-Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=-Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.2, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=-Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive" & 
                            Test == "cPass"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative" & 
                            Test == "cPass"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  theme(legend.position = "none") +
  ylab("Ro-N-Ig") +
  xlab("GS-cPass")
p7f

#----------------------------------------------- Fig7 - G

# Roche vs. LineBlot MG-RBD
p7g <- lab.long.wo %>% filter(Test %in% c("Roche", "LineBlot_RBD_SARS_2")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(x = "value", y = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) + 
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_vline(data = filter(thresholds.now, Test %in%  "LineBlot_RBD_SARS_2"),
             aes(xintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_vline(data = filter(thresholds.now, Test %in% "LineBlot_RBD_SARS_2"),
             aes(xintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_hline(yintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_hline(yintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.3, show.legend=FALSE, size=3.5) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.2, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_RBD_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  theme(legend.position = "none") +
  ylab("Ro-N-Ig") +
  xlab("MG-RBD") +
  scale_x_log10(breaks=c(0.5,  1, 3, 10), labels=c("<1", "1", "3", "10"))
p7g

#----------------------------------------------- Fig7 - H
# Roche vs. LineBlot MG-N
p7h <- lab.long.wo %>% filter(Test %in% c("Roche", "LineBlot_NP_SARS_2")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(x = "value", y = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) + 
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_vline(xintercept=thresholds$Manufacturer[thresholds$Test == "LineBlot_NP_SARS_2"],
             lty=style$thr_lt_old, color=style$thr_lc_old) +
   geom_vline(xintercept=thresholds$Optimized[thresholds$Test=="LineBlot_NP_SARS_2"],
             lty=style$thr_lt_new, color=style$thr_lc_new)  +
  # geom_hline(yintercept = thresholds$Manufacturer[thresholds$Test == v.now],
  #            color=style$thr_lc_old, lty=style$thr_lt_old) +
  # geom_hline(yintercept = thresholds$Optimized[thresholds$Test == v.now],
  #            color=style$thr_lc_new, lty=style$thr_lt_new) +
   geom_hline(data = filter(thresholds.now, Test %in% v.now),
              aes(yintercept=Manufacturer, lty=style$thr_lb_old),
              color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% v.now),
              aes(yintercept=Optimized, lty=style$thr_lb_new),
              color=style$thr_lc_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=2.3, show.legend=FALSE, size=3.5) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=-0.2, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=-0.1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-0.1, show.legend=FALSE, size=3.5) +
  geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative" & 
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.3, show.legend=FALSE, size=3.5) +
  theme(legend.position = "bottom") +
  ylab("Ro-N-Ig") +
  xlab("MG-N") +
  scale_x_log10(breaks=c(0.5,  1, 3, 10), labels=c("<1", "1", "3", "10"))
p7h

legend.p7 <- cowplot::get_legend(p7h)
legend.p7
grid.newpage()
grid.draw(legend.p7)
p7h <- p7h + theme(legend.position="none")
p7h

#------------- multifigure compilation


plot_grid(
  plot_grid(
    title_plot("A", p7a),
    title_plot("B", p7b),
    title_plot("C", p7c),
    title_plot("D", p7d),
    nrow=1, rel_widths = c(0.25,0.25, 0.25, 0.25)),
  plot_grid(
    title_plot("E", p7e),
    title_plot("F", p7f), 
    title_plot("G", p7g),
    title_plot("H", p7h), 
    nrow=1, rel_widths = c(0.25, 0.25, 0.25, 0.25)),
  plot_grid(
    legend.p7, nrow=1),
  nrow=3, rel_heights = c(0.475, 0.475, 0.05))

#ggsave("lab-fig7-201016.pdf", width=12, height=7)
#ggsave("lab-fig7-201016.png", width=12, height=7)
ggsave(here_out("Lab-Figure7.png"), width=14, height=7, units="in")
ggsave(here_out("Lab-Figure7.pdf"), width=14, height=7, units="in")

# Calculate number in plot B
test <- lab %>%
  select(IgG, cPass, `Ground truth`) %>%
  filter(`Ground truth` != "True-negative") %>%
  filter(!is.na(cPass) & !is.na(IgG)) %>%
  filter(cPass < thresholds$Optimized[thresholds$Test == "cPass"]) %>%
  filter(IgG > thresholds$Optimized[thresholds$Test == "IgG"])
table(test$`Ground truth`)  

# Calculate number in plot C
test <- lab %>%
  select(IgG, LineBlot_RBD_SARS_2, `Ground truth`) %>%
  filter(`Ground truth` != "True-negative") %>%
  filter(!is.na(LineBlot_RBD_SARS_2) & !is.na(IgG)) %>%
  filter(LineBlot_RBD_SARS_2 < thresholds$Optimized[thresholds$Test == "LineBlot_RBD_SARS_2"]) %>%
  filter(IgG > thresholds$Optimized[thresholds$Test == "IgG"])
table(test$`Ground truth`)  
```


### Scatterplot Euroimmun IgG and Roche with algorithm results for all studies

```{r, fig.width = 8, fig.height = 3, results = FALSE, echo=FALSE, warning=FALSE}
lab %>%
  mutate(Classifier = case_when(
    IgG >= thresholds$Optimized[thresholds$Test == "IgG"] & 
      Roche >= thresholds$Optimized[thresholds$Test == "Roche"] ~ 
      "Both positives", 
    IgG >= thresholds$Optimized[thresholds$Test == "IgG"] & 
      Roche < thresholds$Optimized[thresholds$Test == "Roche"] ~ 
      "IgG Positive",
    IgG < thresholds$Optimized[thresholds$Test == "IgG"] & 
      Roche >= thresholds$Optimized[thresholds$Test == "Roche"] ~ 
      "Roche Positive",
    IgG < thresholds$Optimized[thresholds$Test == "IgG"] & 
      Roche < thresholds$Optimized[thresholds$Test == "Roche"] ~ "Both negatives")) %>%
  filter(!is.na(Classifier)) %>%
   ggplot(aes(x=Roche, y=IgG, color = Classifier)) +
  geom_point(alpha = 0.5) +
  scale_x_log10() + scale_y_log10() +
  ylab("EI-S1-IgG") + xlab("Ro-N-Ig") +
  theme_bw() +
  scale_color_manual(values = style$pal4[c(2,1,3,4)]) +
  stat_quadrant_counts(
    yintercept = log(thresholds$Optimized[thresholds$Test == "IgG"]), 
    xintercept = log(thresholds$Optimized[thresholds$Test == "Roche"]),
    colour="black", size=3) +
  geom_hline(data = filter(thresholds, Test == "IgG"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "IgG"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == "Roche"], color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == "Roche"],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) 
  

```

### Scatterplot Roche/IgG vs the confirmatory test results (for Manufacturer cutoffs)

```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

lab %>%
  mutate(NT = as.character(NT),
         NT = ifelse(NT == "<10", "5",
                     ifelse(NT == ">80", "80", NT))) %>%
  mutate(NT = as.numeric(NT)) %>%
  tidyr::gather(Test, value, 
                c(IgA, cPass, NT,
                  VC_S1_IgA, VC_S2_IgA, 
                  VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, 
                  VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  left_join(thresholds) %>%
  left_join(Test.names) %>%
  mutate(name = fct_inorder(name)) %>%
  mutate(Result = case_when(
    value < Manufacturer ~ "Negative",
    value >= Manufacturer ~ "Positive",
    is.na(value) ~ "Not performed")) %>%
  #mutate(Test = gsub("_", " ", Test)) %>%
  ggplot(aes(x=Roche, y = IgG, color = Result)) +
  geom_point(data = .%>% filter(Result %in% "Not performed"), alpha=0.3) +
  geom_point(data = .%>% filter(Result %in% "Negative"), alpha=0.3) +
  geom_point(data = .%>% filter(Result %in% "Positive"), alpha=0.3) +
  scale_y_log10() + scale_x_log10() +
  ylab("EI-S1-IgG") + xlab("Ro-N-Ig") +
  geom_hline(data = thresholds %>%
               filter(Test == "IgG") %>%
               select(-Test),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = thresholds %>%
               filter(Test == "IgG") %>%
               select(-Test),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == "Roche"], color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == "Roche"],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  facet_wrap(~name, ncol=5) +
  theme_bw() + theme(legend.position="bottom") +
  scale_color_manual(values=c("#009E73", "grey", "#CC6666")) +
#  scale_color_manual(values=style$pal3[c(2,1,3)]) +
  ggtitle("Binary results based on Manufacturer cut-off")
ggsave(here_out("Fig-SI-7A.pdf"), width=10, height=6)
ggsave(here_out("Fig-SI-7A.png"), width=10, height=6)
```


### Scatterplot Roche/IgG vs the confirmatory test results (for Optimized cutoffs)

```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}
lab %>%
  mutate(NT = as.character(NT),
         NT = ifelse(NT == "<10", "5",
                     ifelse(NT == ">80", "80", NT))) %>%
  mutate(NT = as.numeric(NT)) %>%
  tidyr::gather(Test, value, 
                c(IgA, cPass, NT,
                  VC_S1_IgA, VC_S2_IgA, VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
                  Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  left_join(thresholds) %>%
   left_join(Test.names) %>%
  mutate(name = fct_inorder(name)) %>%
  mutate(Result = case_when(
    value < Optimized ~ "Negative",
    value >= Optimized ~ "Positive",
    is.na(value) ~ "Not performed")) %>%
 # mutate(Test = gsub("_", " ", Test)) %>%
  ggplot(aes(x=Roche, y = IgG, color = Result)) +
  geom_point(data = .%>% filter(Result %in% "Not performed"), alpha=0.3) +
  geom_point(data = .%>% filter(Result %in% "Negative"), alpha=0.3) +
  geom_point(data = .%>% filter(Result %in% "Positive"), alpha=0.3) +
  scale_y_log10() + scale_x_log10() +
  ylab("EI-S1-IgG") + xlab("Ro-N-Ig") +
  geom_hline(data = thresholds %>%
               filter(Test == "IgG") %>%
               select(-Test),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = thresholds %>%
               filter(Test == "IgG") %>%
               select(-Test),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new) +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == "Roche"], color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == "Roche"],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  facet_wrap(~name, ncol=5) +
  theme_bw() + theme(legend.position="bottom") +
   scale_color_manual(values=c("#009E73", "grey", "#CC6666")) +
#  scale_color_manual(values=style$pal3[c(2,1,3)]) +
  ggtitle("Binary results based on Optimized cut-off")
ggsave(here_out("Fig-SI-7B.pdf"), width=10, height=6)
ggsave(here_out("Fig-SI-7B.png"), width=10, height=6)
```


### SI Figs 6 and 10

```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

############# Both optimized and manufacturer together
lab.long.wo <- lab.long.wo %>%
  left_join(Test.names) %>%
  select(-Test) %>%
  rename(Test = name)
thresholds <- thresholds %>%
  left_join(Test.names) %>%
  select(-Test) %>%
  rename(Test = name)

for(v in 1:length(unique(lab.long.wo$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Manufacturer cutoff
 counts <- counts %>%
  # filter(Type %in% "Manufacturer") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   group_by(Type) %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test),
        Type = unique(counts$Type))
 
 counts <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage)) %>%
   ungroup()
 
 counts.man <- counts %>%
   filter(Type %in% "Manufacturer") %>%
   select(Test, `Ground truth`, Percentage, quadrant) %>%
   rename(Percentage.man = Percentage)
 counts.opt <- counts %>%
   filter(Type %in% "Optimized") %>%
   select(Test, `Ground truth`, Percentage, quadrant) %>%
   rename(Percentage.opt = Percentage)
 
 counts.now <- left_join(counts.man, counts.opt) %>%
   mutate(Percentage.man = paste0(as.character(round(Percentage.man, 0)), "%"),
          Percentage.opt = paste0(as.character(round(Percentage.opt, 0)), "%")) %>%
   mutate(Percentage = paste0(Percentage.man, " (", Percentage.opt, ")"))
 
 thresholds.now <- thresholds %>%
     filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plot
  plots.round <- lab.long.wo %>% 
    spread(Test, value) %>%
    gather(Test, value, -c(tln_ID, blut_ID, 
                           `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>%
    droplevels() %>%
    ggplot(aes(y = value, x = !!rlang::sym(v.now),
                    color = `Ground truth`)) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.3,0.3))) + 
  scale_x_log10(expand=expansion(mult=c(0.3,0.3))) +
  facet_wrap(~Test, scales="free", ncol=5) +
  theme_bw() +
   scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test != v.now), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds.now, Test != v.now), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("Measurement value") + xlab(v.now) +
    ggtitle(v.now) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive"),
            aes(x=Inf, y=Inf, label=Percentage),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=Inf, label=Percentage), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-positive"),
            aes(x=0, y=Inf, label=Percentage),
            hjust=-0.1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-negative"),
            aes(x=0, y=Inf, label=Percentage), 
            hjust=-0.1, vjust=2.3, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-positive"),
            aes(x=0, y=0, label=Percentage),
            hjust=-0.1, vjust=-0.1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-negative"),
            aes(x=0, y=0, label=Percentage), 
            hjust=-0.1, vjust=-1.3, show.legend=FALSE, size=3.5) +
       geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-positive"),
            aes(x=Inf, y=0, label=Percentage),
            hjust=1, vjust=-0.1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=0, label=Percentage), 
            hjust=1, vjust=-1.3, show.legend=FALSE, size=3.5)
    # scale_linetype_manual(name="Threshold",
     #                    values=c(style$thr_lt_old,style$thr_lt_new))
 # print(plots.round)
  ggsave(file=here_out(paste0("Fig-scatterplots-all-", v.now, ".pdf")),
         plots.round, width=15, height=8)
  ggsave(file=here_out(paste0("Fig-scatterplots-all-", v.now, ".png")),
         plots.round, width=15, height=8)
}


```


### Scatterplot Roche/IgG vs the confirmatory test results (binary) for each Ground truth category (true negative, true positive, or unknown)

```{r, fig.width = 20, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

lab %>%
  tidyr::gather(Test, Result, 
                c(IgA, cPass, NT, 
                  VC_S1_IgA, VC_S2_IgA, 
                  VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, 
                  VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  left_join(thresholds) %>%
  mutate(Result = case_when(
    Result < Optimized ~ "Negative",
    Result >= Optimized ~ "Positive",
    is.na(Result) ~ "Not performed")) %>%
  #mutate(Test = gsub(".bin", "", Test)) %>%
  #mutate(Test = gsub("_result2", "", Test)) %>%
  mutate(Test = gsub("_", " ", Test)) %>%
  ggplot(aes(x=Roche, y = IgG, color = Result)) +
  geom_point(data = .%>% filter(Result %in% "Not performed"), alpha=0.4) +
  geom_point(data = .%>% filter(Result %in% c("Positive", "Negative")),
             alpha=0.5) +
  scale_y_log10() + scale_x_log10() +
  ylab("Euroimmun S1 IgG") + xlab("Roche N pan-Ig") +
  geom_hline(data = thresholds %>%
               filter(Test == "IgG") %>%
               select(-Test),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = thresholds %>%
               filter(Test == "IgG") %>%
               select(-Test),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == "Roche"], color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == "Roche"],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  facet_grid(`Ground truth`~Test) +
  theme_bw() +
  scale_color_manual(values=style$pal3[c(2,1,3)]) +
  ggtitle("Results based on Optimized cut-off")
```


### Scatterplots Roche vs. the confirmatory test results (continuous values) and clasifying by the Ground truth.

```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

lab %>%
  tidyr::gather(Test, value, 
                c(IgG, IgA, cPass, 
                  VC_S1_IgA, VC_S2_IgA,  
                  VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, 
                  VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
                  Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  left_join(thresholds) %>%
  #mutate(Test = gsub("_", " ", Test)) %>%
  ggplot(aes(y=value, x = Roche, color = `Ground truth`)) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10() + scale_x_log10() +
  facet_wrap(~Test, scales="free", ncol=5) +
  theme_bw() +
  geom_hline(data = filter(thresholds, Test != c("Roche", "NT")),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test != c("Roche", "NT")),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == "Roche"], color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == "Roche"],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  ylab("Test concentration") + xlab("Roche N pan-Ig") 
```


### Threshold counts and percentages by Quadrant

```{r}
v <- 1

v.now <- unique(lab.long.wo$Test)[v]
no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()

counts.gt <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
counts <- left_join(counts.quadrants, counts.gt) %>%
    mutate(Percentage = N.gt / N * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  
counts %>% 
  ggplot(aes(x=Percentage, y=Test,
             color=`Ground truth`,
             shape=Type, group=interaction(Test, `Ground truth`))) +
    geom_point(position=position_dodge(width=0.5)) +
  geom_line() +
    facet_grid(Position~Roche) +
  scale_color_manual(values=style$pal3) +
  ggtitle(v.now) +
  theme_bw() + ylab("")
#ggsave("Percentage-GT-quadrants-Roche.pdf", width=8, height=5)


v.now <- unique(lab.long.wo$Test)[v]
no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  
counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()

counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  
counts %>% 
  ggplot(aes(x=Percentage, y=Test,
             color=`Ground truth`,
             shape=Type, 
             group=interaction(Test, `Ground truth`))) +
  geom_point(position=position_dodge(width=0.5)) +
  geom_line(position=position_dodge(width=0.5)) +
    facet_grid(Position~Roche) +
  scale_color_manual(values=style$pal3) +
  ggtitle(v.now) +
  theme_bw() + ylab("")
#ggsave("Percentage-quadrants-Roche.pdf", width=8, height=5)

v.now <- unique(lab.long.wo$Test)[v]
counts <- counts %>%
   filter(Type %in% "Manufacturer") %>%
   rename(Position.main = Roche)
counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
counts <- counts %>%
   select(-Position, -Position.main)
  
 

lab.long.wo %>% 
    spread(Test, value) %>%
    gather(Test, value, -c(tln_ID, blut_ID, 
                           `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>%
    droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, 
                    color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10() + scale_x_log10() +
   expand_limits(x=1000) +
  facet_wrap(~Test, scales="free", ncol=5) +
  theme_bw() +
  geom_hline(data = filter(thresholds, Test != v.now), 
             aes(yintercept=Manufacturer), color="black", lty=2) +
  geom_hline(data = filter(thresholds, Test != v.now), 
             aes(yintercept=Optimized), color="grey30", lty=3) +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color="black", lty=2) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color="grey30", lty=3) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  ylab("Measurement value") + xlab(v.now) +
    ggtitle(v.now) +
    geom_text(data = filter(counts, quadrant == 1 & 
                              `Ground truth` == "True-positive"),
            aes(x=Inf, y=Inf, label=paste(floor(Percentage), "%")),
            hjust=1, vjust=1) +
    geom_text(data = filter(counts, quadrant == 1 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=Inf, label=paste(floor(Percentage), "%")), 
            hjust=1, vjust=2) +
    geom_text(data = filter(counts, quadrant == 2 & 
                              `Ground truth` == "True-positive"),
            aes(x=0, y=Inf, label=paste(floor(Percentage), "%")),
            hjust=0, vjust=1) +
    geom_text(data = filter(counts, quadrant == 2 & 
                              `Ground truth` == "True-negative"),
            aes(x=0, y=Inf, label=paste(floor(Percentage), "%")), 
            hjust=0, vjust=2) +
    geom_text(data = filter(counts, quadrant == 3 & 
                              `Ground truth` == "True-positive"),
            aes(x=0, y=0, label=paste(floor(Percentage), "%")),
            hjust=0, vjust=0) +
    geom_text(data = filter(counts, quadrant == 3 & 
                              `Ground truth` == "True-negative"),
            aes(x=0, y=0, label=paste(floor(Percentage), "%")), 
            hjust=0, vjust=-1) +
       geom_text(data = filter(counts, quadrant == 4 & 
                              `Ground truth` == "True-positive"),
            aes(x=Inf, y=0, label=paste(floor(Percentage), "%")),
            hjust=1, vjust=0) +
    geom_text(data = filter(counts, quadrant == 4 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=0, label=paste(floor(Percentage), "%")), 
            hjust=1, vjust=-1) 
#ggsave("Quadrant-percentage-Roche.pdf", width=15, height=8)


######### Make a loop on this one
################################# Manufacturer
lab.long.wo <- lab.long.wo %>%
  left_join(Test.names) %>%
  select(-Test) %>%
  rename(Test = name)
thresholds <- thresholds %>%
  left_join(Test.names) %>%
  select(-Test) %>%
  rename(Test = name)

for(v in 1:length(unique(lab.long.wo$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>%
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Manufacturer cutoff
 counts <- counts %>%
   filter(Type %in% "Manufacturer") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))
 
 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage)) 
 
 thresholds.now <- thresholds %>%
     filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plot
   plots.round <- lab.long.wo %>% 
    spread(Test, value) %>%
    gather(Test, value, -c(tln_ID, blut_ID, 
                           `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>%
    droplevels() %>%
  ggplot(aes(y = value, x = !!rlang::sym(v.now), 
                    color = `Ground truth`)) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) + 
  scale_x_log10(expand=expansion(mult=c(0.2,0.2))) +
  facet_wrap(~Test, scales="free", ncol=5) +
  theme_bw() +
   scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test != v.now), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds.now, Test != v.now), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("Measurement value") + xlab(v.now) +
    ggtitle(v.now) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                            `Ground truth` == "True-positive"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-positive"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                            `Ground truth` == "True-negative"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=0, vjust=2.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-positive"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                            `Ground truth` == "True-negative"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=0, vjust=-1.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-positive"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 4 & 
                            `Ground truth` == "True-negative"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.15, show.legend=FALSE, size=3.5)
     # scale_linetype_manual(name="Threshold",
     #                    values=c(style$thr_lt_old,style$thr_lt_new))
 # print(plots.round)
  ggsave(file=here_out(paste0("Fig-scatterplots-Manufacturer-", v.now, ".pdf")), 
         plots.round, width=15, height=8)
  ggsave(file=here_out(paste0("Fig-scatterplots-Manufacturer-", v.now, ".png")), 
         plots.round, width=15, height=8)
}

################################# Optimised
for(v in 1:length(unique(lab.long.wo$Test))){
  v.now <- unique(lab.long.wo$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long.wo %>% 
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>% 
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID, 
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))
  
  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()
  
  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now), 
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))
 
 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))
 
 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT") 
  # End dealing with counts in each quadrant
  # Start plot
   plots.round <- lab.long.wo %>% 
    spread(Test, value) %>%
    gather(Test, value, -c(tln_ID, blut_ID, 
                           `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>%
    droplevels() %>%
  ggplot(aes(y = value, x = !!rlang::sym(v.now),
                    color = `Ground truth`)) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.2,0.2))) + 
  scale_x_log10(expand=expansion(mult=c(0.2,0.2))) +
  #scale_y_continuous(expand = expansion(mult = c(0, 0.1)))
  #expand_limits(x=1000) +
  facet_wrap(~Test, scales="free", ncol=5) +
  theme_bw() +
   scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test != v.now), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds.now, Test != v.now), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("Measurement value") + xlab(v.now) +
    ggtitle(v.now) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-positive"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 1 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=2.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-positive"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 2 & 
                              `Ground truth` == "True-negative"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")), 
            hjust=0, vjust=2.15, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-positive"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 3 & 
                              `Ground truth` == "True-negative"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=0, vjust=-1.15, show.legend=FALSE, size=3.5) +
       geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-positive"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE, size=3.5) +
    geom_text(data = filter(counts.now, quadrant == 4 & 
                              `Ground truth` == "True-negative"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")), 
            hjust=1, vjust=-1.15, show.legend=FALSE, size=3.5)
     # scale_linetype_manual(name="Threshold",
     #                    values=c(style$thr_lt_old,style$thr_lt_new))
 # print(plots.round)
  ggsave(file=here_out(paste0("Fig-scatterplots-Optimized-", v.now, ".pdf")), 
         plots.round, width=15, height=8)
  ggsave(file=here_out(paste0("Fig-scatterplots-Optimized-", v.now, ".png")), 
         plots.round, width=15, height=8)
}


```



### Scatterplots for NT vs. the other test results (continuous values) and clasifying by the Ground truth.

```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

lab.long %>%
  spread(Test, value) %>%
  mutate(NT = factor(NT, levels=c("<10", "10", "20", "40", ">80"))) %>%
  gather(Test, value, c(Roche, IgG, IgA, cPass, 
                  VC_S1_IgA, VC_S2_IgA,  
                  VC_N_IgA, VC_S1_IgM, 
                  VC_S2_IgM, VC_N_IgM, 
                  VC_S1_IgG, VC_S2_IgG, 
                  VC_N_IgG, LineBlot_NP_SARS_2,
                  LineBlot_RBD_SARS_2, LineBlot_S1_SARS_2,
                  Schnupfen_NP_229E, Schnupfen_NP_NL63, 
                  Schnupfen_NP_OC43, Schnupfen_NP_HKU1)) %>%
  mutate(value = as.numeric(value)) %>%
  left_join(Test.names) %>%
  select(-Test) %>%
  rename(Test = name) %>%
  left_join(thresholds) %>%
  filter(!is.na(NT)) %>%
  ggplot(aes(y=value, x = NT, color = `Ground truth`)) +
  geom_jitter(alpha=0.5) +
  facet_wrap(~Test, scales="free") +
  ylab("Test value") +
  #  geom_flat_violin(fill=style$col_grey, col=style$col_grey, 
  #                   position = position_nudge(x = .02, y = 0),
  #                   alpha=0.3, trim=F, scale="area") +
  #  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
  #                   fill=style$col_truepos, col=style$col_truepos, 
  #                   position = position_nudge(x = .02, y = 0),
  #                   alpha=0.3, trim=F, scale="area") +
  #  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
  #                   fill=style$col_trueneg, col=style$col_trueneg, 
  #                   position = position_nudge(x = .02, y = 0),
  #                   alpha=0.3, trim=F, scale="area") + 
  # # Jitter points on the left
   # geom_point(aes(x=as.numeric(NT)-0.25, y=value,
   #                col=`Ground truth`),
   #            position = position_jitter(width = .17, ), alpha=0.5) +
   scale_color_manual(values=style$pal3) +
  geom_hline(data = thresholds %>% filter(Test != "NT"), 
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = thresholds %>% filter(Test != "NT"), 
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  scale_y_log10()


```




### Plots for Figure 7 (old)


```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}

# for Roche in x-axis
v <- 1
#for(v in 1:length(unique(lab.long$Test))){
  v.now <- unique(lab.long$Test)[v]
  # Deal with counts at each quadrant
  no.se.que <- lab.long %>%
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>%
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID,
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))

  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()

  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now),
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))

 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))

 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT")
  # End dealing with counts in each quadrant
  # Start plots

# Roche vs. cPass
p1 <- lab.long %>% filter(Test %in% c("Roche", "cPass")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) +
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_x_log10() +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "cPass"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "cPass"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 1 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=2, show.legend=FALSE) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 &
                            `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 2 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=2, show.legend=FALSE) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 &
                            `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=0, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 3 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=0, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-1, show.legend=FALSE) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 &
                            `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=Inf, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 4 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=Inf, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-1, show.legend=FALSE) +
  theme(legend.position = "none") +
  xlab(v.now) +
  ylab("GS-cPass")
p1

# Roche vs. VC N IgG
p2 <- lab.long %>% filter(Test %in% c("Roche", "VC_N_IgG")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "VC_N_IgG"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "VC_N_IgG"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("VC N IgG") + xlab(v.now) +
  geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-1, show.legend=FALSE) +
       geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-1, show.legend=FALSE) +
  theme(legend.position = "none")
 p2


# Roche vs. LineBlot NP
p3 <- lab.long %>% filter(Test %in% c("Roche", "LineBlot_NP_SARS_2")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(breaks=c(0.5, 1, 3, 10), labels=c("<1", "1", "3", "10"),
                expand=expansion(mult=c(0.15,0.15))) +
  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "LineBlot_NP_SARS_2"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "LineBlot_NP_SARS_2"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("LineBlot NP") + xlab(v.now) +
  geom_text(data= filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-1, show.legend=FALSE) +
       geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-1, show.legend=FALSE) +
  theme(legend.position="none")
 p3


# For D) NT vs Roche
no.se.que <- lab %>%
  select(tln_ID, blut_ID, NT, Roche, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, NT)) %>%
  left_join(thresholds) %>%
  mutate(quadrant = case_when(
    value < Optimized & NT == "<10" ~ "<10-below",
    value >= Optimized & NT == "<10" ~ "<10-above",
    value < Optimized & NT == "10" ~ "10-below",
    value >= Optimized & NT == "10" ~ "10-above",
    value < Optimized & NT == "20" ~ "20-below",
    value >= Optimized & NT == "20" ~ "20-above",
    value < Optimized & NT == "40" ~ "40-below",
    value >= Optimized & NT == "40" ~ "40-above",
    value < Optimized & NT == ">80" ~ ">80-below",
    value >= Optimized & NT == ">80" ~ ">80-above")) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant))
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n())
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100)
counts
# For the column-wise n
cwn <- counts.quadrant %>%
  mutate(category = gsub("-.+", "", quadrant)) %>%
  group_by(category) %>%
  summarize(n.total = sum(n))
cwn
p4 <- lab %>%
  filter(!is.na(NT)) %>%
  mutate(NT = factor(as.character(NT),
                      levels = c("<10", "10", "20", "40", ">80"))) %>%
  ggplot(aes(y=Roche, x=NT, color=`Ground truth`)) +
  # Violin plots on the right
  geom_flat_violin(fill=style$col_grey, col=style$col_grey,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
                   fill=style$col_truepos, col=style$col_truepos,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
                   fill=style$col_trueneg, col=style$col_trueneg,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  # Jitter points on the left
  geom_point(aes(x=as.numeric(NT)-0.25, y=Roche,
                 col=`Ground truth`),
             position = position_jitter(width = .17, ), alpha=0.5) +
  scale_color_manual(values=style$pal3) +
  geom_hline(data = filter(thresholds, Test == "Roche"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "Roche"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new))  +
  theme(legend.position="none") +
  geom_text(data = filter(counts, quadrant == "<10-below" &
                            `Ground truth` == "True-negative"),
            aes(x=1.15, y=0.005, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts, quadrant == "<10-above" &
                            `Ground truth` == "True-negative"),
            aes(x=1.15, y=1500, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts, quadrant == "<10-above" &
                            `Ground truth` == "True-positive"),
            aes(x=1.15, y=1500, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "10-above" &
                            `Ground truth` == "True-positive"),
            aes(x=2.15, y=1500, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "20-above" &
                            `Ground truth` == "True-positive"),
            aes(x=3.15, y=1500, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "40-above" &
                            `Ground truth` == "True-positive"),
            aes(x=4.15, y=1500, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE)  +
  geom_text(data = filter(counts, quadrant == ">80-above" &
                            `Ground truth` == "True-positive"),
            aes(x=5.15, y=1500, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  scale_y_log10(breaks=c(0.05, 1, 10, 100, 1000),
                labels=c("0.05", "1", "10", "100", "1000")) +
  annotate("text", x=c(1:5), y=4500, size=3,
           label=c(paste("n=", cwn$n.total)))

p4

# for IgG in x-axis
v <- 2
#for(v in 1:length(unique(lab.long$Test))){
  v.now <- unique(lab.long$Test)[v]
  v.now
  # Deal with counts at each quadrant
  no.se.que <- lab.long %>%
    left_join(gather(thresholds, Type, Threshold, -Test)) %>%
    mutate(Position = ifelse(value >= Threshold, "Above", "Below")) %>%
    select(-value, -Threshold) %>%
    spread(Test, Position) %>%
    gather(Test, Position, -c(tln_ID, blut_ID,
                           `Ground truth`, Type, v.now)) %>%
    filter(Test != v.now) %>%
    filter(!is.na(Position)) %>%
    filter(!is.na(!!rlang::sym(v.now)))

  counts.gt.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Position", "Ground truth", v.now)) %>%
    summarize(N=n()) %>%
    ungroup()
  counts.quadrants <- no.se.que %>%
    group_by_at(c("Type", "Test", "Ground truth")) %>%
    summarize(N.gt=n())  %>%
    ungroup()

  counts <- left_join(counts.gt.quadrants, counts.quadrants) %>%
    mutate(Percentage = N / N.gt * 100) %>%
    mutate(!!v.now := factor(!!rlang::sym(v.now),
                             levels=c("Below", "Above")))
  # Here I select the Optimized cutoff
 counts <- counts %>%
   filter(Type %in% "Optimized") %>%
   rename(Position.main = !!rlang::sym(v.now))

 counts <- counts %>%
   mutate(quadrant = case_when(
     Position == "Above" & Position.main == "Above" ~ 1,
     Position == "Above" & Position.main == "Below" ~ 2,
     Position == "Below" & Position.main == "Below" ~ 3,
     Position == "Below" & Position.main == "Above" ~ 4))
 counts <- counts %>%
   select(-Position, -Position.main)

 full.quadrants <- expand.grid(quadrant = 1:4,
        `Ground truth` = levels(counts$`Ground truth`),
        Test = unique(counts$Test))

 counts.now <- filter(counts, Test != v.now) %>%
  droplevels() %>%
   full_join(full.quadrants) %>%
   mutate(Percentage = ifelse(is.na(Percentage), 0, Percentage))
 thresholds.now <- thresholds %>%
    filter(Test != "NT")
  # End dealing with counts in each quadrant
  # Start plots

# IgG vs. cPass
p5 <- lab.long %>% filter(Test %in% c("IgG", "cPass")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  #scale_y_continuous(expand=expansion(mult=c(2,2))) +
#  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_x_log10() +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "cPass"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "cPass"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("cPass") + xlab(v.now) +
  # 1st quadrant
  geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 1 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=2, show.legend=FALSE) +
  # 2nd quadrant
  geom_text(data = filter(counts.now, quadrant == 2 &
                            `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 2 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=2, show.legend=FALSE) +
  # 3rd quadrant
  geom_text(data = filter(counts.now, quadrant == 3 &
                            `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=0, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 3 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=0, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-1, show.legend=FALSE) +
  # 4th quadrant
  geom_text(data = filter(counts.now, quadrant == 4 &
                            `Ground truth` == "True-positive" &
                            Test == "cPass"),
            aes(x=Inf, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts.now, quadrant == 4 &
                            `Ground truth` == "True-negative" &
                            Test == "cPass"),
            aes(x=Inf, y=-Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-1, show.legend=FALSE) +
  theme(legend.position="none")
p5

# IgG vs. VC N IgG
p6 <- lab.long %>% filter(Test %in% c("IgG", "VC_N_IgG")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "VC_N_IgG"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "VC_N_IgG"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("VC N IgG") + xlab(v.now) +
  geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=Inf, label=paste(floor(Percentage), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-1, show.legend=FALSE) +
       geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-positive" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-negative" &
                            Test == "VC_N_IgG"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-1, show.legend=FALSE) +
  theme(legend.position="none")

p6


# IgG vs. LineBlot NP
p7 <- lab.long %>% filter(Test %in% c("IgG", "LineBlot_NP_SARS_2")) %>% spread(Test, value) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, v.now)) %>%
    filter(Test != v.now) %>% droplevels() %>%
  ggplot(aes_string(y = "value", x = v.now, color = "`Ground truth`")) +
  geom_point(data = .%>% filter(`Ground truth` == "Unknown"), alpha=0.5) +
  geom_point(data = .%>% filter(`Ground truth` != "Unknown"), alpha=0.5) +
  scale_y_log10(breaks=c(0.5, 1, 3, 10), labels=c("<1", "1", "3", "10"),
                expand=expansion(mult=c(0.15,0.15))) +
  scale_x_log10(expand=expansion(mult=c(0.15,0.15))) +
  scale_colour_manual(values=style$pal3[c(2, 3, 1)]) +
  geom_hline(data = filter(thresholds.now, Test %in%  "LineBlot_NP_SARS_2"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
   geom_hline(data = filter(thresholds.now, Test %in% "LineBlot_NP_SARS_2"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  geom_vline(xintercept = thresholds$Manufacturer[thresholds$Test == v.now],
             color=style$thr_lc_old, lty=style$thr_lt_old) +
  geom_vline(xintercept = thresholds$Optimized[thresholds$Test == v.now],
             color=style$thr_lc_new, lty=style$thr_lt_new) +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new)) +
  ylab("LineBlot NP") + xlab(v.now) +
  geom_text(data= filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 1 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=1, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 2 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=Inf, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=2, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 3 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=0, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=0, vjust=-1, show.legend=FALSE) +
       geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-positive" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
    geom_text(data = filter(counts.now, quadrant == 4 &
                              `Ground truth` == "True-negative" &
                            Test == "LineBlot_NP_SARS_2"),
            aes(x=Inf, y=0, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=-1, show.legend=FALSE) +
  theme(legend.position="none")

p7


# For D) NT vs IgG
no.se.que <- lab %>%
  select(tln_ID, blut_ID, NT, IgG, `Ground truth`) %>%
  gather(Test, value, -c(tln_ID, blut_ID, `Ground truth`, NT)) %>%
  left_join(thresholds) %>%
  mutate(quadrant = case_when(
    value < Optimized & NT == "<10" ~ "<10-below",
    value >= Optimized & NT == "<10" ~ "<10-above",
    value < Optimized & NT == "10" ~ "10-below",
    value >= Optimized & NT == "10" ~ "10-above",
    value < Optimized & NT == "20" ~ "20-below",
    value >= Optimized & NT == "20" ~ "20-above",
    value < Optimized & NT == "40" ~ "40-below",
    value >= Optimized & NT == "40" ~ "40-above",
    value < Optimized & NT == ">80" ~ ">80-below",
    value >= Optimized & NT == ">80" ~ ">80-above")) %>%
  select(quadrant, `Ground truth`) %>%
  filter(!is.na(quadrant))
counts.quadrant <- no.se.que %>%
  group_by(quadrant, `Ground truth`) %>%
  summarize(n=n())
counts.gt <- no.se.que %>%
  group_by(`Ground truth`) %>%
  summarize(n.total=n())
counts <- left_join(counts.quadrant, counts.gt) %>%
  mutate(Percentage = n / n.total * 100)
counts
# For the column-wise n
cwn <- counts.quadrant %>%
  mutate(category = gsub("-.+", "", quadrant)) %>%
  group_by(category) %>%
  summarize(n.total = sum(n))
cwn
p8 <- lab %>%
  filter(!is.na(NT)) %>%
  mutate(NT = factor(as.character(NT),
                      levels = c("<10", "10", "20", "40", ">80"))) %>%
  ggplot(aes(y=IgG, x=NT, color=`Ground truth`)) +
  # Violin plots on the right
  geom_flat_violin(fill=style$col_grey, col=style$col_grey,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-positive"),
                   fill=style$col_truepos, col=style$col_truepos,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  geom_flat_violin(data = .%>% filter(`Ground truth` == "True-negative"),
                   fill=style$col_trueneg, col=style$col_trueneg,
                   position = position_nudge(x = .02, y = 0),
                   alpha=0.3, trim=F, scale="area") +
  # Jitter points on the left
  geom_point(aes(x=as.numeric(NT)-0.25, y=IgG,
                 col=`Ground truth`),
             position = position_jitter(width = .17, ), alpha=0.5) +
  scale_color_manual(values=style$pal3) +
  geom_hline(data = filter(thresholds, Test == "IgG"),
             aes(yintercept=Manufacturer, lty=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_hline(data = filter(thresholds, Test == "IgG"),
             aes(yintercept=Optimized, lty=style$thr_lb_new),
             color=style$thr_lc_new)  +
  scale_linetype_manual(name="Threshold",
                        values=c(style$thr_lt_old, style$thr_lt_new))  +
  theme(legend.position="none") +
  scale_y_log10() +
  geom_text(data = filter(counts, quadrant == "<10-below" &
                            `Ground truth` == "True-negative"),
            aes(x=1.15, y=0.02, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=1, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "<10-below" &
                          `Ground truth` == "True-positive"),
            aes(x=1.15, y=0.02, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "<10-above" &
                          `Ground truth` == "True-positive"),
            aes(x=1.15, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "10-above" &
                            `Ground truth` == "True-positive"),
            aes(x=2.15, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "20-above" &
                            `Ground truth` == "True-positive"),
            aes(x=3.15, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  geom_text(data = filter(counts, quadrant == "40-above" &
                            `Ground truth` == "True-positive"),
            aes(x=4.15, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE)  +
  geom_text(data = filter(counts, quadrant == ">80-above" &
                          `Ground truth` == "True-positive"),
            aes(x=5.15, y=35, label=paste(round(Percentage, 0), "%")),
            hjust=1, vjust=0, show.legend=FALSE) +
  annotate("text", x=c(1:5), y=75, size=3,
           label=c(paste("n=", cwn$n.total)))


p8

plot_grid(p1, p2, p3, p5, p6, p7, p4, p8, legend,
          labels=c("A", "B", "C", "D", "E", "F", "G", "H"),
          nrow=3)
#ggsave("lab-fig7-201008.pdf", width=10, height=8)
#ggsave("lab-fig7-201008.png", width=10, height=8)
```


### Density plot for all the tests regarding the ground truth


```{r, fig.width = 10, fig.height = 6, results = FALSE, echo=FALSE, warning=FALSE}
lab %>%
  select(IgA, IgG, Roche, cPass, #NT, 
         VC_S1_IgA, VC_S2_IgA, VC_N_IgA,
         VC_S1_IgG, VC_S2_IgG, VC_N_IgG,
         VC_S1_IgM, VC_S2_IgM, VC_N_IgM,
         LineBlot_NP_SARS_2, LineBlot_RBD_SARS_2,
         LineBlot_S1_SARS_2,
         Schnupfen_NP_229E, Schnupfen_NP_NL63, 
         Schnupfen_NP_OC43, Schnupfen_NP_HKU1,
         `Ground truth`) %>%
  gather(Test, value, -`Ground truth`) %>%
  mutate(Test = gsub("_", " ", Test)) %>%
  ggplot(aes(x=value, fill=`Ground truth`, color=`Ground truth`)) +
  geom_density(alpha=0.5) +
  facet_wrap(~Test, scales="free") +
  theme_bw() + 
  scale_x_log10() +
  scale_fill_manual(values=style$pal3) +
  scale_colour_manual(values=style$pal3) +
  xlab("Test concentration") + ylab("Density")

```


```{r, fig.width = 20, fig.height = 20, results = FALSE, echo=FALSE, warning=FALSE}

p <- lab %>%
  filter(!is.na(NT)) %>%
  select(IgA, IgG, Roche, cPass, NT,
         VC_S1_IgA, VC_S2_IgA, VC_N_IgA,
         VC_S1_IgG, VC_S2_IgG, VC_N_IgG,
         VC_S1_IgM, VC_S2_IgM, VC_N_IgM,
         LineBlot_NP_SARS_2, LineBlot_RBD_SARS_2,
         LineBlot_S1_SARS_2, `Ground truth`) %>%
  mutate(CPass = case_when(
    cPass <= 0 ~ 0.1,
    cPass > 0 ~ cPass)) %>%
   mutate(IgA = log(IgA), IgG = log(IgG), Roche = log(Roche),
          cPass = log(cPass), VC_S1_IgA = log(VC_S1_IgA), 
          VC_S2_IgA = log(VC_S2_IgA), VC_N_IgA = log(VC_N_IgA),
          VC_S1_IgG = log(VC_S1_IgG), VC_S2_IgG = log(VC_S2_IgG),
          VC_N_IgG = log(VC_N_IgG), VC_S1_IgM = log(VC_S1_IgM),
          VC_S2_IgM = log(VC_S2_IgM), VC_N_IgM = log(VC_N_IgM),
          LineBlot_NP_SARS_2 = log(LineBlot_NP_SARS_2),
          LineBlot_RBD_SARS_2 = log(LineBlot_RBD_SARS_2),
          LineBlot_S1_SARS_2 = log(LineBlot_S1_SARS_2)) %>%
  ggpairs(mapping=aes(colour = `Ground truth`)) +
  theme_bw() 

for(i in 1:p$nrow) {
  for(j in 1:p$ncol){
    p[i,j] <- p[i,j] + 
        scale_fill_manual(values=style$pal3) +
        scale_color_manual(values=style$pal3)  
  }
}
#p

ggsave(file=here_out("Full-scatterplots.pdf"), p, 
       width=24, height=18)
```
