---
title: "Lab Paper 1st part"
author: "Yannik Schälte"
output:
  html_document:
    toc: true
    toc_float: true
---

Compilation date: `r format(Sys.time(), '%d.%m.%Y')`

The figures used in the lab manuscript are generated in the last section of
the notebook, the previous parts creating subplots and detailed analyses.

# Prepare

```{r}
here_r = function (...) here::here("Statistics", "R", ...)
here_lab_data = function (...) here::here("Lab_paper2_data", ...)
here_out = function (...) here::here(
  "Lab_paper2_output", "lab_figures_yannik", ...)

library(magrittr)
library(ggplot2)
library(cowplot)
library(dplyr)

# Load settings
source(here_r("setup.R"))
source(here_r("functions.R"))

# Load half violin package
source(here_r("RainCloudPlots", "R_rainclouds.R"))

# Load data
#  Single data contains only one blood sample per participant
single_data = read.csv(here_lab_data(
  "Global_Data", "New_NT_category", "Final_Lab_Single_20200904_NT.csv"), stringsAsFactors = F)

###############################################################################
# Clean data

data = single_data

#  Unique labels
data[data=="Positiv" | data=="pos." | data=="reactive" |
     data=="positive"] = "Positive"
data[data=="Negativ" | data=="Indeterminate" | data=="neg." | data=="ind." | 
     data=="nonreactive" | data=="negative"] = "Negative"

#  Remove Roche 0 values
val_cols = grep("roche_COI", colnames(data), value=T)
res_cols = grep("roche_Interpretation", colnames(data), value=T)
cat("# Roche == 0 before removal:", sum(data[,val_cols]==0, na.rm=T), "\n")
for (j in 1:length(val_cols)) {
  # Conveniently, the order is the same
  val_col = val_cols[[j]]
  res_col = res_cols[[j]]
  data[data[,val_col]==0 & !is.na(data[,val_col]), res_col] = NA
  data[data[,val_col]==0 & !is.na(data[,val_col]), val_col] = NA
}

#  Add binary ground truth column
data['Ground truth'] = ifelse(
  is.na(data$model_outcome), "Unknown",
        ifelse(data$model_outcome=="true_positive", "True-positive",
               "True-negative"))
data$`Ground truth` = factor(
  as.character(data$`Ground truth`),
  levels = c("Unknown", "True-negative", "True-positive"))

#  NT to categories with correct ordering
data$NT = as.character(data$NT)
# rename 1:5 -> 5
data[!is.na(data$NT) & data$NT=='1:5', 'NT'] = '5'
data$NT = factor(data$NT, levels = c("<5", "5", "10", "20", "40", ">80"))

###############################################################################
# Check data consistency

# Assertions
if (length(unique(single_data$blut_ID)) != nrow(single_data)) {
  stop("Blood id not unique")
}
if (length(unique(single_data$tln_ID)) != nrow(single_data)) {
  stop("Participant id not unique")
}

#' Check consistency of reported values according to assumed thresholds
check_consistency = function(val_cols, res_cols, threshold) {
  for (j in 1:length(val_cols)) {
    # Assuming that value and result columns have the same order
    val_col = val_cols[[j]]
    res_col = res_cols[[j]]
    by_value = sum(data[,val_col]>=threshold, na.rm=T)
    by_cat = sum(data[,res_col] == "Positive", na.rm=T)
    if (by_value != by_cat) {
      stop(paste("Mismatch positives (exp./act.)", by_value, by_cat))
    }
    by_value = sum(data[,val_col]<threshold, na.rm=T)
    by_cat = sum(data[,res_col] == "Negative", na.rm=T)
    if (by_value != by_cat) {
      stop(paste("Mismatch negatives (exp./act.)", by_value, by_cat))
    }
  }
}

#  Roche
val_cols = grep("roche_COI", colnames(data), value=T)
res_cols = grep("roche_Interpretation", colnames(data), value=T)
check_consistency(val_cols, res_cols, 1.0)
if (any(data[,val_cols]==0, na.rm=T)) {
  stop("There are Roche zero values.")
}

#  Euroimmun
val_cols = grep("eur_quotient", colnames(data), value=T)
res_cols = grep("eur_der_test_result", colnames(data), value=T)
check_consistency(val_cols, res_cols, 1.1)
if (any(data[,val_cols]==0, na.rm=T)) {
  stop("There are Euroimmun zero values.")
}

# Use corrected data frame
single_data = data

###############################################################################
# Some statistics
cat("# rows:", nrow(single_data), "\n")
cat("# columns:", ncol(single_data), "\n")
cat("# Ground truths:", sum(!is.na(single_data$model_outcome)),
    sum(single_data$`Ground truth`!="Unknown"), "\n")
cat("# True-positive:", sum(single_data$`Ground truth`=="True-positive"), "\n")
cat("# True-negative:", sum(single_data$`Ground truth`=="True-negative"), "\n")

# Tidy up
rm(data, val_cols, res_cols, val_col, res_col, j)
```

# Duplicate concordance analysis

Here, we look at concordance between repeated measurements of a test, i.e. replicate values taken from the same blood sample. We look at Euroimmun IgA and IgG, and Roche IgG measurements. To ensure sample independence, we consider only one blood sample per participant.

## EI-S1-IgA and -IgG measurements

Prepare data:

```{r}
# Rows are samples, columns repetitions (max 3)
# Interesting columns: eur_quotient_i_{IgA,IgG}
mult_euro = single_data[,grep("eur", colnames(single_data))]

# Values data frame
mult_euro_val = mult_euro[,grep("eur_quotient", colnames(mult_euro))]
## Prettify column names to "Ig{A,G} {1,2,3}"
colnames(mult_euro_val) = paste(
  substr(colnames(mult_euro_val), 16, 18),
  substr(colnames(mult_euro_val), 14, 14), sep=" ")

# How many values are there for the different replicates?
for (col in colnames(mult_euro_val)) {
  cat(col, sum(!is.na(mult_euro_val[,col])), "\n")
}

# Too few cases of replicate 3 -> disregard
mult_euro_val = mult_euro_val[,!grepl("3", colnames(mult_euro_val))]

# Tidy up
rm(col)
```

Scatter plots:

```{r, fig.height=3.5, fig.width=7}
# Scatter plots
plt_iga = scatter(mult_euro_val, "IgA 1", "IgA 2",
                  "Replicate 1", "Replicate 2",
                  cutoff1=cutoff$old$Eur_IgA, cutoff2=cutoff$old$Eur_IgA,
                  stat_x=-1.5, stat_y=0.6,
                  ann_x=c(0.5, 2, 0.5, 2), ann_y=c(0.08, 0.08, 10, 10),
                  title="EI-S1-IgA replicates")
plt_igg = scatter(mult_euro_val, "IgG 1", "IgG 2",
                  "Replicate 1", "Replicate 2",
                  cutoff1=cutoff$old$Eur_IgG, cutoff2=cutoff$old$Eur_IgG,
                  stat_x=-1.5, stat_y=0.6,
                  ann_x=c(0.5, 2, 0.5, 2), ann_y=c(0.08, 0.08, 10, 10),
                  title="EI-S1-IgG replicates")

# Correlation plot
corr = Hmisc::rcorr(as.matrix(log10(mult_euro_val)), type="pearson")
ggcorrplot::ggcorrplot(
  corr$r, type="lower", show.diag=T, lab=T,
  legend.title="", title="Pearson correlations")

# Merge plots
plt_rep_eur = ggpubr::ggarrange(plt_iga, plt_igg, nrow=1)
plt_rep_eur

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Euroimmun_Scatter.", fmt)),
  #       device=fmt, dpi=style$dpi, width=7, height=3.5, units="in")
}

# Tidy up
rm(plt_iga, plt_igg, corr, fmt)
```

```{r}
rbind(
  qualitative_2x2_table(mult_euro_val, "IgA 1", "IgA 2", cutoff$old$Eur_IgA,
                        cutoff$old$Eur_IgA, label="IgA 1/2, Old threshold"),
  qualitative_2x2_table(mult_euro_val, "IgA 1", "IgA 2", cutoff$new$Eur_IgA,
                        cutoff$new$Eur_IgA, label="IgA 1/2, New threshold"),
  qualitative_2x2_table(mult_euro_val, "IgG 1", "IgG 2", cutoff$old$Eur_IgG,
                        cutoff$old$Eur_IgG, label="IgG 1/2, Old threshold"),
  qualitative_2x2_table(mult_euro_val, "IgG 1", "IgG 2", cutoff$new$Eur_IgG,
                        cutoff$new$Eur_IgG, label="IgG 1/2, New threshold")
)
```

CAPTION: Scatter plots of two Euroimmun S1 IgA and Euroimmun S1 IgG measurement replicates, for the same blood sample. The blue lines indicate linear regression lines with standard errors. Pearson correlation coefficients R of the log-scaled values are also indicated in the plot. Dashed lines indicate manufacturer decision thresholds (value of 1.1 for both IgA and IgG). The numbers n indicate the numbers of points in the respective quadrants.

The correlations are good, in particular for IgG, while IgA shows more variability. IgA-IgG correlations are lower, as expected, as these measure two different features.

The scatter plots allow to assess how far off the diagonal the values are.

All integrated in a single plot:

```{r, fig.width=6, fig.height=6}
#PerformanceAnalytics::chart.Correlation(log10(mult_euro_val), histogram=T)
```

Having looked so far at the quantitative results, next, we create contingency tables of the qualitative results. For simple visualization of the agreement, we use a bar plot of the percentages.

Here we use the old cut-off, as we want to compare the values of the manufacturer directly.

```{r, fig.width=4, fig.height=3.5}
# Create categorical result data frame
data = mult_euro_val
iga_cols = grep("IgA", colnames(data), value=T)
igg_cols = grep("IgG", colnames(data), value=T)
data[,iga_cols] = ifelse(data[,iga_cols]>=cutoff$old$Eur_IgA,
                         "Positive", "Negative")
data[,igg_cols] = ifelse(data[,igg_cols]>=cutoff$old$Eur_IgG,
                         "Positive", "Negative")

# Create contingency matrices in data frame (separate IgA and IgG)
contis = create_contingency_matrix(data, classifiers=c("IgA", "IgG"))
# To long format
contis_long = reshape2::melt(contis, id.vars=c("Methods", "total"), 
                             value.name="Percentage")
colnames(contis_long)[colnames(contis_long) == "variable"] = "Outcomes"

# Prettify
contis_long$Methods = stringr::str_replace_all(
  contis_long$Methods, c(" & "=" \n& ", "1"="Rep. 1", "2"="Rep. 2"))

# Remember
contis_long_euroimmun = contis_long

ggplot(contis_long,
       aes(fill=Outcomes, color=Outcomes, x=Methods, y=Percentage)) +
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  geom_text(data=contis_long[!duplicated(contis_long$Methods),],
            aes(x=Methods, y=1.05, label=total), color="black") +
  scale_y_continuous(labels=scales::percent) +
  scale_fill_manual(values=style$pal4, ) + 
  scale_color_manual(values=style$pal4, )

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Euroimmun_Bar.", fmt)),
  #       device=fmt, dpi=style$dpi, width=4, height=3.5, units="in")
}

rm(data, iga_cols, igg_cols, contis, contis_long, fmt)
```

CAPTION: Qualitative agreement of the outcome of Euroimmun S1 IgA and Euroimmun S1 IgG measurement replicates.

We see that for IgA there are batch effects.

## Ro-N-Ig

Now, we repeat basically the same for Roche. Here, we have in total 2 machines, each with up to 4 measurements (but a lot of sparsity).
Prepare data:

```{r}
mult_roche = single_data[,c("machine_1", "machine_2",
                            grep("roche_COI", colnames(single_data), value=T))]

old_machine_cols =
  c("roche_COI_1_1", "roche_COI_2_1", "roche_COI_3_1", "roche_COI_4_1")
new_machine_cols =
  c("roche_COI_1_2", "roche_COI_2_2", "roche_COI_3_2", "roche_COI_4_2")

if (nrow(mult_roche[mult_roche$machine_1=="new" &
                    !is.na(mult_roche$machine_2),]) > 0) {
  stop("The Roche machine assignment is wrong.")
}

# move values where machine 1 is "new" to the second set of entries
mult_roche[mult_roche$machine_1=="new" &
           !is.na(mult_roche$machine_1), new_machine_cols] =
  mult_roche[mult_roche$machine_1=="new" &
             !is.na(mult_roche$machine_1), old_machine_cols]
# and remove old entries
mult_roche[mult_roche$machine_1=="new" &
           !is.na(mult_roche$machine_1), old_machine_cols] = NA

# Add columns aggregating machine 1 and machine 2
df = mult_roche
mult_roche$M2 =
  ifelse(!is.na(df$roche_COI_4_2), df$roche_COI_4_2,
         ifelse(!is.na(df$roche_COI_3_2), df$roche_COI_3_2,
                ifelse(!is.na(df$roche_COI_2_2), df$roche_COI_2_2,
                       df$roche_COI_1_2)))
mult_roche$M1 =
  ifelse(!is.na(df$roche_COI_4_1), df$roche_COI_4_1,
         ifelse(!is.na(df$roche_COI_3_1), df$roche_COI_3_1,
                ifelse(!is.na(df$roche_COI_2_1), df$roche_COI_2_1,
                       df$roche_COI_1_1)))

# Add columns aggregating replicates
mult_roche$Rep1 =
  ifelse(!is.na(df$roche_COI_1_2), df$roche_COI_1_2, df$roche_COI_1_1)
mult_roche$Rep2 =
  ifelse(!is.na(df$roche_COI_2_2), df$roche_COI_2_2, df$roche_COI_2_1)
mult_roche$Rep3 =
  ifelse(!is.na(df$roche_COI_3_2), df$roche_COI_3_2, df$roche_COI_3_1)
mult_roche$Rep4 =
  ifelse(!is.na(df$roche_COI_4_2), df$roche_COI_4_2, df$roche_COI_4_1)

# Simplify column names
rep_cols = paste(
  "Roche", substr(grep("COI", colnames(mult_roche), value=T), 11, 13))
colnames(mult_roche)[grep("COI", colnames(mult_roche))] = rep_cols

# How many values are there for the different replicates?
for (col in rep_cols) {
  cat(col, sum(!is.na(mult_roche[,col])), "\n")
}
# intersections (rep. 3 and 4 have too few entries)
rep_cols = paste("Roche", c("1_1", "2_1", "1_2", "2_2"))
for (i in 1:(length(rep_cols)-1)) {
  for (j in (i+1):length(rep_cols)) {
    cat(rep_cols[i], "&", rep_cols[j],
        sum(!is.na(mult_roche[,rep_cols[i]]) &
            !is.na(mult_roche[,rep_cols[j]])), "\n")
  }
}
cat("Roche M1 & M2",
    sum(!is.na(mult_roche[,"M1"]) & !is.na(mult_roche[,"M2"])), "\n")
cat("Roche Rep1 & Rep2",
    sum(!is.na(mult_roche[,"Rep1"]) & !is.na(mult_roche[,"Rep2"])), "\n")

rm(col, rep_cols, i, j, df, old_machine_cols, new_machine_cols)
```

### Scatter plots for single replicates

```{r, fig.height=3.5, fig.width=10.5}
# Scatter plots
plt_11_21 = scatter(mult_roche, "Roche 1_1", "Roche 2_1",
                    name1="Machine 1, Replicate 1",
                    name2="Machine 1, Replicate 2",
                    cutoff1=cutoff$old$Roche, cutoff2=cutoff$old$Roche,
                    stat_x=0.1, stat_y=-0.5,
                    ann_x=c(0.3, 3, 0.3, 3), ann_y=c(0.08, 0.08, 50, 50))
plt_11_12 = scatter(mult_roche, "Roche 1_1", "Roche 1_2",
                    name1="Machine 1, Replicate 1",
                    name2="Machine 2, Replicate 1",
                    cutoff1=cutoff$old$Roche, cutoff2=cutoff$old$Roche,
                    stat_x=0.1, stat_y=-0.5,
                    ann_x=c(0.3, 3, 0.3, 3), ann_y=c(0.08, 0.08, 50, 50))
plt_12_22 = scatter(mult_roche, "Roche 1_2", "Roche 2_2",
                    name1="Machine 2, Replicate 1",
                    name2="Machine 2, Replicate 2",
                    cutoff1=cutoff$old$Roche, cutoff2=cutoff$old$Roche,
                    stat_x=0.1, stat_y=-0.5,
                    ann_x=c(0.3, 3, 0.3, 3), ann_y=c(0.08, 0.08, 50, 50))

# Merge plots
plt = ggpubr::ggarrange(plt_11_21, plt_11_12, plt_12_22, nrow=1)
plt

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Roche_Scatter_Single.", fmt)),
  #       device=fmt, dpi=style$dpi, width=10.5, height=3.5, units="in")
}

# Tidy up
rm(plt_11_21, plt_11_12, plt_12_22, plt, fmt)
```

CAPTION: Scatter plots of Roche N IgG measurement replicates, either on the same machine (left), or across machines (right). The repeated measurements were performed using the same blood sample. The blue lines indicate linear regression lines with standard errors. Pearson correlation coefficients R and associated p-value of the log-scaled values are also indicated in the plot. Dashed lines indicate manufacturer decision thresholds (value of 1.0). The numbers n indicate the numbers of points in the respective quadrants.

### Scatter plots condensed to Machine / Replicate comparison

```{r, fig.height=3.5, fig.width=7}
# Scatter plots
plt_m = scatter(mult_roche, "M1", "M2",
                name1="Machine 1", name2="Machine 2",
                title="Ro-N-Ig machines",
                cutoff1=cutoff$old$Roche, cutoff2=cutoff$old$Roche,
                stat_x=0.1, stat_y=-0.5,
                ann_x=c(0.3, 3, 0.3, 3), ann_y=c(0.08, 0.08, 50, 50))
plt_r = scatter(mult_roche, "Rep1", "Rep2",
                name1="Replicate 1", name2="Replicate 2",
                title="Ro-N-Ig: replicates",
                cutoff1=cutoff$old$Roche, cutoff2=cutoff$old$Roche,
                stat_x=0.1, stat_y=-0.5,
                ann_x=c(0.3, 3, 0.3, 3), ann_y=c(0.08, 0.08, 50, 50))
plt_rep_roche = ggpubr::ggarrange(plt_m, plt_r, nrow=1)
plt_rep_roche

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Roche_Scatter.", fmt)),
  #       device=fmt, dpi=style$dpi, width=7, height=3.5, units="in")
}

rm(plt_m, plt_r, fmt)
```

```{r}
rbind(
  qualitative_2x2_table(mult_roche, "Roche 1_1", "Roche 2_1", cutoff$old$Roche,
                        cutoff$old$Roche, label="Roche 1_1/2_1, Old threshold"),
  qualitative_2x2_table(mult_roche, "Roche 1_1", "Roche 2_1", cutoff$new$Roche,
                        cutoff$new$Roche, label="Roche 1_1/2_1, New threshold"),
  qualitative_2x2_table(mult_roche, "Roche 1_1", "Roche 1_2", cutoff$old$Roche,
                        cutoff$old$Roche, label="Roche 1_1/1_2, Old threshold"),
  qualitative_2x2_table(mult_roche, "Roche 1_1", "Roche 1_2", cutoff$new$Roche,
                        cutoff$new$Roche, label="Roche 1_1/1_2, New threshold")
)
```

### Bar plot for single replicates

```{r, fig.width=5, fig.height=3.5}
# Create categorical result data frame
data_res = mult_roche[paste("Roche", c("1_1", "2_1", "1_2", "2_2"))]
data_res = ifelse(data_res>=cutoff$old$Roche, "Positive", "Negative")

# Create contingency matrices in data frame
contis = create_contingency_matrix(data_res)
# To long format
contis_long = reshape2::melt(contis, id.vars=c("Methods", "total"), 
                             value.name="Percentage")
colnames(contis_long)[colnames(contis_long) == 'variable'] = "Outcomes"

# Remove 1_2 vs 2_1 which has only 2 entries
contis_long = contis_long[
  contis_long$Methods %in%c("Roche 1_1 & Roche 1_2", "Roche 1_1 & Roche 2_1",
                            "Roche 1_2 & Roche 2_2"),]

# Prettify Method names
contis_long$Methods = stringr::str_replace_all(
  contis_long$Methods,
  c(" & "="\n& ", "Roche 1_1"="M. 1 Rep. 1", "Roche 1_2"="M. 2 Rep. 1",
    "Roche 2_1"="M. 1 Rep. 2", "Roche 2_2"="M. 2 Rep. 2"))

# Remember  
contis_long_roche = contis_long

ggplot(contis_long, aes(fill=Outcomes, color=Outcomes,
                        x=Methods, y=Percentage)) +
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  scale_y_continuous(labels=scales::percent) +
  geom_text(data=contis_long[!duplicated(contis_long$Methods),],
            aes(x=Methods, y=1.05, label=total), color="black") +
  scale_fill_manual(values=style$pal4) + scale_color_manual(values=style$pal4)

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Roche_Bar_Single.", fmt)),
  #device=fmt, dpi=style$dpi, width=4, height=3.5, units="in")
}

rm(data_res, contis, contis_long, fmt)
```

CAPTION: Qualitative agreement of the outcome of Roche N measurement replicates. The manufacturer decision thresholds were used to decide whether a test is positive or negative.

# Bar plots condensed to Machine / Replicate comparison

```{r, fig.width=4.5, fig.height=3.5}
# Create categorical result data frame
data_res = mult_roche[c("M1", "M2", "Rep1", "Rep2")]
data_res = ifelse(data_res>=cutoff$old$Roche, "Positive", "Negative")

# Create contingency matrices in data frame
contis = create_contingency_matrix(data_res)
# To long format
contis_long = reshape2::melt(contis, id.vars=c("Methods", "total"),
                             value.name="Percentage")
colnames(contis_long)[colnames(contis_long) == 'variable'] = "Outcomes"

# Remove 1_2 vs 2_1 which has only 2 entries
contis_long = contis_long[
  contis_long$Methods %in% c("M1 & M2", "Rep1 & Rep2"),]

# Remember
contis_long_roche_2 = contis_long

ggplot(contis_long,
       aes(fill=Outcomes, color=Outcomes, x=Methods, y=Percentage)) +
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  scale_y_continuous(labels=scales::percent) +
  geom_text(data=contis_long[!duplicated(contis_long$Methods),],
            aes(x=Methods, y=1.05, label=total), color="black") +
  scale_fill_manual(values=style$pal4) + scale_color_manual(values=style$pal4)

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Roche_Bar.", fmt)),
  #       device=fmt, dpi=style$dpi, width=4, height=3.5, units="in")
}

rm(data_res, contis, contis_long, fmt)
```

## Qualitative plot for Euroimmun and Roche combined

### With single Roche replicates

```{r, fig.width=7, fig.height=3.5}
contis_long = rbind(contis_long_euroimmun, contis_long_roche)

# Clean up labels
contis_long[contis_long=="IgA Rep. 1 \n& IgA Rep. 2"] =
  "EI-S1-IgA:\nRep. 1 & 2"
contis_long[contis_long=="IgG Rep. 1 \n& IgG Rep. 2"] =
  "EI-S1-IgG:\nRep. 1 & 2"
contis_long[contis_long=="M. 1 Rep. 1\n& M. 1 Rep. 2"] =
  "Ro-N-Ig:\nM. 1 Rep. 1 & 2"
contis_long[contis_long=="M. 1 Rep. 1\n& M. 2 Rep. 1"] =
  "Ro-N-Ig:\nM. 1 & 2 Rep. 1"
contis_long[contis_long=="M. 2 Rep. 1\n& M. 2 Rep. 2"] =
  "Ro-N-Ig:\nM. 2 Rep. 1 & 2"

# Prettiy columns names
colnames(contis_long)[colnames(contis_long)=="Outcomes"] ="Test outcomes"
colnames(contis_long)[colnames(contis_long)=="Methods"] = "Tests"

ggplot(contis_long, aes(fill=`Test outcomes`, color=`Test outcomes`, 
                        x=Tests, y=Percentage)) +
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  scale_y_continuous(labels=scales::percent) +
  geom_text(data=contis_long[!duplicated(contis_long$Tests),],
            aes(x=Tests, y=1.05, label=total), color="black") +
  scale_fill_manual(values=style$pal4) + scale_color_manual(values=style$pal4)

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Main_Bar_Single.", fmt)),
  #device=fmt, dpi=style$dpi, width=7, height=3.5, units="in")
}

rm(contis_long, fmt)
```

### With Roche reduced

```{r, fig.width=5, fig.height=3.5}
contis_long = rbind(contis_long_euroimmun, contis_long_roche_2)

# Clean up labels
contis_long[contis_long=="IgA Rep. 1 \n& IgA Rep. 2"] = "EI-S1-IgA:\nRep. 1 & 2"
contis_long[contis_long=="IgG Rep. 1 \n& IgG Rep. 2"] = "EI-S1-IgG:\nRep. 1 & 2"
contis_long[contis_long=="M1 & M2"] = "Ro-N-Ig:\nM. 1 & 2"
contis_long[contis_long=="Rep1 & Rep2"] = "Ro-N-Ig:\nRep. 1 & 2"

# Remove machine comparison
contis_long = contis_long[contis_long$Methods!="Ro-N-Ig:\nM. 1 & 2",]

# Prettiy columns names
colnames(contis_long)[colnames(contis_long)=="Outcomes"] = "Test outcomes"
colnames(contis_long)[colnames(contis_long)=="Methods"] = "Tests"

plt_rep_bar = ggplot(contis_long, aes(fill=`Test outcomes`, color=`Test outcomes`, x=Tests, y=Percentage)) +
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  scale_y_continuous(labels=scales::percent) +
  geom_text(data=contis_long[!duplicated(contis_long$Tests),],
            aes(x=Tests, y=1.05, label=total), color="black") +
  scale_fill_manual(values=style$pal4) + scale_color_manual(values=style$pal4) +
  labs(x="")
plt_rep_bar

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Replicates_Main_Bar.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6, height=3.5, units="in")
}

rm(contis_long, fmt)
```

## Qualitative plot colored by ground truth

Excluded. There seem to be no replicates for true negatives

```{r}
# data = single_data 
# 
# old_machine_cols = c("roche_COI_1_1", "roche_COI_2_1",
#                      "roche_COI_3_1", "roche_COI_4_1")
# new_machine_cols = c("roche_COI_1_2", "roche_COI_2_2",
#                      "roche_COI_3_2", "roche_COI_4_2")
# 
# # move values where machine 1 is "new" to the second set of entries
# data[data$machine_1=="new" & !is.na(data$machine_1), new_machine_cols] = 
#   data[data$machine_1=="new" & !is.na(data$machine_1), old_machine_cols]
# # and remove old entries
# data[data$machine_1=="new" & !is.na(data$machine_1), old_machine_cols] = NA
# 
# data = data %>% dplyr::rename(
#   "IgA 1"="eur_quotient_1_IgA", "IgA 2"="eur_quotient_2_IgA",
#   "IgG 1"="eur_quotient_1_IgG", "IgG 2"="eur_quotient_2_IgG",
#   "Roche 1_1"="roche_COI_1_1", "Roche 1_2"="roche_COI_1_2",
#   "Roche 2_1"="roche_COI_2_1")
# data = data[data$`Ground truth`!="Unknown",]
# 
# # Get for all combination of measurements an indicator as PP, NP, PN, or NN
# pairs = list(c("IgA 1", "IgA 2"), c("IgG 1", "IgG 2"),
#              c("Roche 1_1", "Roche 1_2"), c("Roche 1_1", "Roche 2_1"))
# cols = unique(unlist(pairs))
# for (col in cols[1:2]) {
#   data[,col] = ifelse(data[,col]>=cutoff$old$Eur_IgA, "Positive", "Negative")
# }
# for (col in cols[3:4]) {
#   data[,col] = ifelse(data[,col]>=cutoff$old$Eur_IgG, "Positive", "Negative")
# }
# for (col in cols[5:7]) {
#   data[,col] = ifelse(data[,col]>=cutoff$old$Roche, "Positive", "Negative")
# }
# 
# pair_cols = c()
# for (pair in pairs) {
#   col1 = pair[1]
#   col2 = pair[2]
#   pair_col = paste(col1, col2, sep=" & ")[1]
#   pair_cols = c(pair_cols, pair_col)
#   data[,pair_col] = 
#     ifelse(data[col1]=="Positive" & data[col2]=="Positive", "PP",
#            ifelse(data[col1]=="Positive" & data[col2]=="Negative", "PN",
#                   ifelse(data[col1]=="Negative" & data[col2]=="Positive", "NP",
#                          ifelse(data[col1]=="Negative" & data[col2]=="Negative",
#                                 "NN", NA))))
# }
# 
# data_long = data %>% tidyr::gather(Methods, Outcomes, pair_cols)
# # Remove NA outcome
# data_long = data_long[!is.na(data_long$Outcomes),]
# 
# ggplot(data=data_long, aes(x=Outcomes, fill=`Ground truth`)) +
#   facet_wrap(~Methods, scales = "free_y") +
#   geom_bar(stat="count", alpha=0.5)
# 
# rm(pair, pairs, pair_cols, data, data_long, old_machine_cols, new_machine_cols,
#    col, cols, col1, col2, pair_col)
```

Clear up

```{r}
rm(contis_long_euroimmun, contis_long_roche, contis_long_roche_2, mult_euro,
   mult_euro_val, mult_roche)
```

# Distribution of main methods

Here, we look at the agreement between the main tests Euroimmun IgA, Euroimmun IgG, and Roche IgG.

```{r, fig.height=3, fig.width=12}
data = extract_last_values(single_data)[,c(columns$main, "Ground truth")]

rec_old = get_recovery_rates(
  data, columns$main, cutoffs=cutoff$old, cutoff_label="Old")
rec_new = get_recovery_rates(
  data, columns$main, cutoffs=cutoff$new, cutoff_label="New")
rownames(rec_old) = rec_old$Method
rownames(rec_new) = rec_new$Method

hist_iga = stacked_distr(
  data=data, col="Eur_IgA", rec_old=rec_old, rec_new=rec_new,
  col_pretty=columns_pretty$eur_iga,
  x_old_pos=1.9, x_old_neg=0.06, x_new_pos=1.9, x_new_neg=0.06, y_txt=800,
  y_pct=850)

hist_igg = stacked_distr(
  data=data, col="Eur_IgG", rec_old=rec_old, rec_new=rec_new,
  col_pretty=columns_pretty$eur_igg,
  x_old_pos=1.9, x_old_neg=0.5, x_new_pos=1.9, x_new_neg=0.5, y_txt=1000,
  y_pct=1050)

hist_roche = stacked_distr(
  data=data, col="Roche", rec_old=rec_old, rec_new=rec_new,
  col_pretty=columns_pretty$roche,
  x_old_pos=2.4, x_old_neg=1/2.4, x_new_pos=2, x_new_neg=1/2, y_txt=3700,
  y_pct=3800, sec_axis_name="Cumulative distribution")

plt_main_distr = ggpubr::ggarrange(hist_iga + theme(legend.position = "none"),
                                   hist_igg + theme(legend.position = "none"),
                                   hist_roche, nrow=1, widths = c(4,4,5.8))
plt_main_distr

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Main_Distribution.", fmt)),
  #       device=fmt, dpi=style$dpi, width=12, height=3, units="in")
}

rm(data, rec_old, rec_new, hist_iga, hist_igg, hist_roche, fmt)
```

CAPTION: Distribution of measurement values for the main methods Euroimmun S1 IgA, Euroimmun S1 IgG, and Roche N. Manufacturer decision thresholds for the respective method are indicated by dashed lines. The colors indicate cases known to be positive or negative, or for which such knowledge is not available. The histograms for all 3 classes are stacked above each other.

## Qualitative agreement of main tests and ground truth

The following is not used.

```{r, fig.width=5, fig.height=3.5}
data = extract_last_values(single_data)
rec = get_recovery_rates(data, columns$main, cutoff$new)
# Total number of cases with measurement and ground truth
rec$total = rec[,"p"] + rec[,"n"]

# To fraction
val_cols = c("p_truepos", "n_truepos", "p_trueneg", "n_trueneg")
rec[,val_cols] = rec[,val_cols] / rec[,"total"]

# To long
rec_long = reshape2::melt(
  rec[,c("Method", "total", val_cols)],
  id.vars=c("Method", "total"), value.name="Percentage")
colnames(rec_long)[colnames(rec_long) == 'variable'] = "Outcomes"

# Prettify
for (i in 1:length(columns$main)) {
  rec_long[rec_long$Method==columns$main[i],"Test"] = columns_pretty$main[i]
}
rec_long$Outcomes = as.character(rec_long$Outcomes)
outcomes_old = c("p_truepos", "n_truepos", "p_trueneg", "n_trueneg")
outcomes_new = c(
  "Test-positive & True-positive", "Test-negative & True-positive",
  "Test-positive & True-negative", "Test-negative & True-negative")
for (i in 1:length(outcomes_old)) {
  rec_long[rec_long==outcomes_old[i]] = outcomes_new[i]
}
rec_long$`Test outcomes` = factor(rec_long$Outcomes, levels=outcomes_new)

ggplot(rec_long, aes(fill=`Test outcomes`, color=`Test outcomes`,
                     x=Test, y=Percentage)) +
  # Stacked percentage bars
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  # Totals
  geom_text(data=rec_long[!duplicated(rec_long$Test),],
            aes(x=Test, y=1.05, label=total), color="black") +
  # Transform y axis labels to percent
  scale_y_continuous(labels=scales::percent) +
  scale_fill_manual(values=style$pal4) +
  scale_color_manual(values=style$pal4) +
  labs(x="")

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Main_GroundTruth_Accordance.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6.5, height=3.5, units="in")
}

rm(data, rec, val_cols, rec_long, outcomes_old, outcomes_new, i, fmt)
```

What is missing here though is a "zoom-in" also on the small percentage of positive cases. So, let's split up into negatives and positives. The following is an alternative to the above figures:

```{r, fig.height=3, fig.width=7}
plt_main_gt_bar = test_gt_bars(
  single_data, columns$main, columns_pretty$main, 3, cutoff)
plt_main_gt_bar

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("GroundTruth_Main_Split_Accordance.", fmt)),
  #       device=fmt, dpi=style$dpi, width=7, height=3.5, units="in")
}

rm(fmt)
```

Exchanging the roles of Test outcome and Ground truth (excluded):

```{r, fig.height=3, fig.width=6}
gt_test_bars(
  single_data, columns$main, columns_pretty$main, 3, cutoff$new, "")
```

# Distribution of confirmatory tests

## NT and cPass

```{r, fig.width=5, fig.height=3}
data = single_data

# Get recovery rates
data_cts = to_numeric(data)
cols = c("cPass", "NT")
rec_old = get_recovery_rates(
  data_cts, cols, cutoffs=cutoff$old, cutoff_label="Old")
rec_new = get_recovery_rates(
  data_cts, cols, cutoffs=cutoff$new, cutoff_label="New")
rownames(rec_old) = rec_old$Method
rownames(rec_new) = rec_new$Method

# NT
plt_nt = ggplot(data %>% dplyr::filter(!is.na(NT)),
                aes(x=NT, color=`Ground truth`, fill=`Ground truth`)) + 
  geom_bar(alpha=0.5) +
  # Thresholds
  #  Only new
  geom_vline(aes(xintercept=1.5, linetype=style$thr_lb_new),
             color=style$thr_lc_new) +
  #  Use linetype aesthetic to create a separate legend
  scale_linetype_manual(name="Cut-off", values=c(style$thr_lt_new)) +
  # Percentage annotations
  annotate("text", size=3, color=style$col_truepos, hjust="left",
            x=1.5 + 0.1, y=200,
           label=sprintf("%.0f%%", rec_new["NT", "frac_pos_rec"] * 100)) +
  annotate("text", size=3, color=style$col_trueneg, hjust="right",
            x=1.5 - 0.1, y=200,
           label=sprintf("%.0f%%", rec_new["NT", "frac_neg_rec"] * 100)) +
  labs(x=paste0(
    columns_pretty$nt, " (n=", sum(!is.na(data$NT)), ")"), y="Count") +
  scale_fill_manual(values=style$pal3) + scale_color_manual(values=style$pal3)
plt_nt

# cPass
plt_cpass = ggplot(data,
                   aes(x=cPass, fill=`Ground truth`, color=`Ground truth`)) +
  geom_histogram(alpha=0.5, position="stack") +  
  # Thresholds
  geom_vline(aes(xintercept=cutoff$old$cPass, linetype=style$thr_lb_old),
             color=style$thr_lc_old) +
  geom_vline(aes(xintercept=cutoff$new$cPass, linetype=style$thr_lb_new),
             color=style$thr_lc_new) +
  #  Use linetype aesthetic to create a separate legend
  scale_linetype_manual(
    name="Cut-off", values=c(style$thr_lt_old,style$thr_lt_new)) +
  annotate("text", size=3, color=style$col_truepos, hjust="center",
            x=cutoff$old$cPass + 10, y=35,
           label=sprintf("%.0f%%", rec_new["cPass", "frac_pos_rec"] * 100)) +
  annotate("text", size=3, color=style$col_trueneg, hjust="center",
            x=cutoff$old$cPass - 30, y=35,
           label=sprintf("%.0f%%", rec_new["cPass", "frac_neg_rec"] * 100)) +
  annotate("text", size=3, color=style$col_truepos, hjust="center",
            x=cutoff$old$cPass + 10, y=30,
           label=sprintf("(%.0f%%)", rec_old["cPass", "frac_pos_rec"] * 100)) +
  annotate("text", size=3, color=style$col_trueneg, hjust="center",
            x=cutoff$old$cPass - 30, y=30,
           label=sprintf("(%.0f%%)", rec_old["cPass", "frac_neg_rec"] * 100)) +
  labs(x=paste0(
    columns_pretty$cpass,
    " [%] (n=", sum(!is.na(data$cPass)), ")"), y="Count") +
  scale_fill_manual(values=style$pal3) + scale_color_manual(values=style$pal3)
plt_cpass

rm(data, data_cts, rec_old, rec_new, cols)
```

CAPTION: Distribution of measurement values for NT and cPass. The dashed lines indicate the respective manufacturer test decision thresholds. Coloring as in Figure TODO.

```{r}
data = to_numeric(single_data)
cols = c("NT", "cPass")
rbind(get_recovery_rates(data, cols, cutoffs=cutoff$old, cutoff_label="Old"),
      get_recovery_rates(data, cols, cutoffs=cutoff$new, cutoff_label="New"))

rm(data, cols)
```

## Array

```{r, fig.height=5, fig.width=12}
cols = columns$vc
cols_pretty = columns_pretty$vc

# Remove the new cutoffs for VC-non-IgG
cutoff_tmp = new.env()
cutoff_tmp$old = cutoff$old
cutoff_tmp$new = cutoff$new
for (col in grep("(IgA|IgM)", columns$vc, value=T)) {
  cutoff_tmp$new[col] = NA
}

data = data_long_for_viola(
  single_data, columns$vc, columns_pretty$vc, "<10", cutoff_tmp)
data_long = data[[1]]
data_long_inv = data[[2]]

# Violin plots and jitter for the continuous part
plt_up = jitter_violin_plot(
  data_long, cols_pretty=cols_pretty,
  ylimits=c(2,1000), ybreaks=c(2.3,10,100,1000),
  ylabels=c("<10","10","100","1000"),
  ymeas=700, thr_shift=0.05)
plt_up

# Histogram for the discrete part
plt_down = discrete_bar_plot(data_long_inv, ylimits=c(0,150))
plt_down

# Insert histogram into the continuous plot (parameters require manual tuning
#  depending on figure size)
plt_vc_distr = plt_up + annotation_custom(
  ggplotGrob(plt_down + theme(legend.position = "none")),
  ymin=0.15, ymax=0.7, xmin=0.3, xmax=9.7)
plt_vc_distr

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Array_Distribution.", fmt)),
  #       device=fmt, dpi=style$dpi, width=12, height=5, units="in")
}

rm(data, data_long, data_long_inv, cols, cols_pretty, cutoff_tmp, plt_up,
   plt_down, fmt, col)
```

CAPTION: Distribution of measurement values for the nine Array tests. The tests do not give quantitative values below 10. Thus, in the lower part histograms over all values classified as <10 are shown. In the upper part, jittered point plots and violin plots are shown. Color coding is as in Figure TODO. The percentage numbers around the threshold lines indicate the percentage of true positives identified as positive according to the threshold (red number above line), resp. the percentage of true negatives identified as negative (blue number below line).

Recovery of true positives and negatives by the 2 thresholds:

```{r}
data = to_numeric(single_data)
get_recovery_rates(data, columns$vc, cutoffs=cutoff$old, cutoff_label="Old")
get_recovery_rates(data, columns$vc, cutoffs=cutoff$new, cutoff_label="New")
rm(data)
```

Restricted to IgG:

```{r, fig.height=3, fig.width=5}
cols = grep("IgG", columns$vc, value=T)
cols_pretty = grep("IgG", columns_pretty$vc, value=T)

data = data_long_for_viola(single_data, cols, cols_pretty, "<10", cutoff)
data_long = data[[1]]
data_long_inv = data[[2]]

# Violin plots and jitter for the continuous part
plt_up = jitter_violin_plot(
  data_long, cols_pretty=cols_pretty,
  ylimits=c(2,1000), ybreaks=c(2.3,10,100,1000),
  ylabels=c("<10","10","100","1000"),
  ymeas=700, thr_shift=0.10, violin_width=0.6)
plt_up

# Histogram for the discrete part
plt_down = discrete_bar_plot(data_long_inv, ylimits=c(0,195))
plt_down

# Insert histogram into the continuous plot (parameters require manual tuning
#  depending on figure size)
plt_vc_distr_igg = plt_up + annotation_custom(
  ggplotGrob(plt_down + theme(legend.position = "none")),
  ymin=0.13, ymax=0.7, xmin=0.3, xmax=3.7)
plt_vc_distr_igg

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Array_Distribution_IgG.", fmt)),
  #       device=fmt, dpi=style$dpi, width=5, height=4, units="in")
}

rm(data, data_long, data_long_inv, cols, cols_pretty, plt_up, plt_down, fmt)
```

## Line blot

```{r, fig.height=3, fig.width=5}
cols = columns$lineblot
cols_pretty = columns_pretty$lineblot

data = data_long_for_viola(
  single_data, cols, cols_pretty, "not_reactive", cutoff)
data_long = data[[1]]
data_long_inv = data[[2]]

# Violin plots and jitter for the continuous part
plt_up = jitter_violin_plot(
  data_long, cols_pretty=cols_pretty,
  ylimits=c(0.3,30), ybreaks=c(0.4,1,3,10),
  ylabels=c("<1","1","3","10"),
  ymeas=30, thr_shift=0.07, violin_width=0.7,
  show_old_percent = F)
plt_up

# Histogram for the discrete part
plt_down = discrete_bar_plot(data_long_inv, ylimits=c(0,170))
plt_down

# Combine plots
plt_lineblot_distr = plt_up + annotation_custom(
  ggplotGrob(plt_down + theme(legend.position = "none")),
  ymin=-0.65, ymax=-0.15, xmin=0.3, xmax=3.7)
plt_lineblot_distr

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("LineBlot_Distribution.", fmt)),
  #       device=fmt, dpi=style$dpi, width=5, height=5, units="in")
}

rm(data, data_long, data_long_inv, cols, cols_pretty, plt_up, plt_down, fmt)
```

CAPTION: Distribution of measurement values for the three Line Blot tests. Figure setup as in Figure TODO.

Recovery of true positives and negatives by the 2 thresholds:

```{r}
data = to_numeric(single_data)
rbind(
  get_recovery_rates(
    data, columns$lineblot, cutoff=cutoff$old, cutoff_label="Old"),
  get_recovery_rates(
    data, columns$lineblot, cutoff=cutoff$new, cutoff_label="New")
)
rm(data)
```

# Common Cold

## Distribution

```{r, fig.height=3, fig.width=6}
cols = columns$cold
cols_pretty = columns_pretty$cold

# add dummy cutoffs, same as for lineblot
cutoff_tmp = cutoff
for (col in cols) { 
  cutoff_tmp$old[col] = 1
  cutoff_tmp$new[col] = NA
}

data = data_long_for_viola(
  single_data, cols, cols_pretty, "not_reactive", cutoff)
data_long = data[[1]]
data_long_inv = data[[2]]

# Violin plots and jitter for the continuous part
plt_up = jitter_violin_plot(
  data_long, cols_pretty=cols_pretty,
  ylimits=c(0.3,30), ybreaks=c(0.4,1,3,10),
  ylabels=c("<1","1","3","10"),
  ymeas=20, thr_shift=0.07, violin_width=0.7,
  show_new_line = F, show_new_percent = F)
plt_up

# Histogram for the discrete part
plt_down = discrete_bar_plot(data_long_inv, ylimits=c(0,120))
plt_down

# Combine plots
plt_cold = plt_up + annotation_custom(
  ggplotGrob(plt_down + theme(legend.position = "none")),
  ymin=-0.67, ymax=-0.23, xmin=0.3, xmax=4.7)
plt_cold

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("CommonCold_Distribution.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6, height=3.5, units="in")
}

rm(data, data_long, data_long_inv, cols, cols_pretty, cutoff_tmp, plt_up,
   plt_down, fmt, col)
```

## Distribution tests

Two-sample Kolmogorov-Smirnov tests of the distributions.

Correction: 

```{r}
data = single_data
# TODO Include these values as 0.5, as KW only needs ranks
data[data=="not_reactive"] = NA
for (col in columns$cold) {
  data[,col] = as.numeric(data[,col])
}

# Kolmogorov-Smirnov
#print("Kolmogorov-Smirnov")
#for (col in columns$cold) {   
#  print(col)
#  positives = data[
#    data["Ground truth"]=="True-positive" & !is.na(data[,col]), col]
#  negatives = data[
#    data["Ground truth"]=="True-negative" & !is.na(data[,col]), col]
#  unknowns = data[
#    data["Ground truth"]=="Unknown" & !is.na(data[,col]), col]
#  print(ks.test(positives, unknowns))
#  print(ks.test(negatives, unknowns))
#  print(ks.test(positives, negatives))
#}

# Kruskal-Wallis / Dunn
print("Kruskal-Wallis / Dunn")
for (col in columns$cold) {
  print(col)
  formula = as.formula(paste(col, "~", "`Ground truth`"))
  print(kruskal.test(formula, data))
  print(FSA::dunnTest(formula, data, method="by"))
}

rm(data, col, formula)
```

## Correlations with Roche

```{r, fig.width=6, fig.height=3.5}
cols = columns$cold
cols_pretty = columns_pretty$cold

# Set discrete values to arbitrary value
data = extract_last_values(single_data)[c("Roche", "Ground truth", cols)]
# Set discrete part to some visually distinguishable value <1
data[data=="not_reactive"] = 0.8
for (col in cols) {
  data[,col] = as.numeric(data[,col])
}

data_long = data %>% tidyr::gather(Test, Value, -c(Roche, `Ground truth`))

# Prettify
for (i in 1:length(cols)) {
  data_long[data_long$Test==cols[i],"Test"] = cols_pretty[i]
}

# Fill non-reactives with NA on copy for statistics
data_long_na = data_long
data_long_na[data_long_na$Value==0.8 & !is.na(data_long_na$Value),"Value"] = NA

plt_cold_roche = ggplot(data_long, aes(x=Roche, y=Value)) +
  facet_wrap(~Test, scales = "free") +
  geom_point(aes(col=`Ground truth`), alpha=0.5) + scale_x_log10() +
  # Regression line
  geom_smooth(formula=y~x, method="lm", data=data_long_na) +
  # Pearson correlation coefficient
  ggpubr::stat_cor(data=data_long_na) +
  scale_y_log10(breaks=c(0.8, 1, 3, 5), labels=c("<1", 1, 3, 5)) +
  labs(y="Line blot", x="Ro-N-Ig") +
  scale_fill_manual(values=style$pal3) + scale_color_manual(values=style$pal3)
plt_cold_roche

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("CommonCold_Roche_Scatter.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6, height=3.5, units="in")
}

rm(data, data_long, data_long_na, fmt, cols, cols_pretty, col, i)
```

## Correlations with IgG

```{r, fig.width=6, fig.height=3.5}
cols = columns$cold
cols_pretty = columns_pretty$cold

# Set discrete values to arbitrary value
data = extract_last_values(single_data)[c("Eur_IgG", "Ground truth", cols)]
# Set discrete part to some visually distinguishable value <1
data[data=="not_reactive"] = 0.8
for (col in cols) {
  data[,col] = as.numeric(data[,col])
}

data_long = data %>% tidyr::gather(Test, Value, -c(Eur_IgG, `Ground truth`))

# Prettify
for (i in 1:length(cols)) {
  data_long[data_long$Test==cols[i],"Test"] = cols_pretty[i]
}

# Fill non-reactives with NA on copy for statistics
data_long_na = data_long
data_long_na[data_long_na$Value==0.8 & !is.na(data_long_na$Value),"Value"] = NA

ggplot(data_long, aes(x=Eur_IgG, y=Value)) +
  facet_wrap(~Test, scales = "free") +
  geom_point(aes(col=`Ground truth`), alpha=0.5) + scale_x_log10() +
  geom_smooth(formula=y~x, method="lm", data=data_long_na) +
  ggpubr::stat_cor(data=data_long_na) +
  scale_y_log10(breaks=c(0.8, 1, 3, 5), labels=c("<1", 1, 3, 5)) +
  labs(y="Line blot", x="Roche N pan-Ig") +
  scale_fill_manual(values=style$pal3) + scale_color_manual(values=style$pal3)

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("CommonCold_EuroimmunIgG_Scatter.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6, height=3.5, units="in")
}

rm(data, data_long, data_long_na, fmt, cols, cols_pretty, col, i)
```

# Comparison of the main tests (Figure 4)

## EI-S1-IgG vs Ro-N-Ig (Excluded)

```{r, fig.width=5, fig.height=3.5}
data = extract_last_values(single_data)[c(columns$main, "Ground truth")]

# Prettify
for (i in 1:length(columns$main)) {
  colnames(data)[colnames(data)==columns$main[i]] = columns_pretty$main[i]
}

plt_roche_igg = ggplot(data, aes(x=`Ro-N-Ig`, y=`EI-S1-IgG`)) +
  geom_point(aes(col=`Ground truth`), alpha=0.5) +
  scale_x_log10() + scale_y_log10() +
  # Threshold lines
  geom_vline(aes(xintercept = cutoff$old$Roche),
             linetype = style$thr_lt_old, color=style$thr_lc_old) +
  geom_vline(aes(xintercept = cutoff$new$Roche),
             linetype = style$thr_lt_new, color=style$thr_lc_new) +
  geom_hline(aes(yintercept = cutoff$old$Eur_IgG,
                 linetype = style$thr_lb_old), color=style$thr_lc_old) +
  geom_hline(aes(yintercept = cutoff$new$Eur_IgG,
                 linetype = style$thr_lb_new), color=style$thr_lc_new) +
  scale_linetype_manual(
    name="Cut-off", values=c(style$thr_lt_old,style$thr_lt_new)) +
  #geom_smooth(formula=y~x, method="lm") +
  ggpubr::stat_cor() +
  scale_fill_manual(values=style$pal3) + scale_color_manual(values=style$pal3)
plt_roche_igg

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Roche_EuroimmunIgG_Scatter.", fmt)),
  #       device=fmt, dpi=style$dpi, width=5, height=3.5, units="in")
}

cols = c(columns_pretty$eur_igg, columns_pretty$roche)
# Correlation of all (as in plot)
Hmisc::rcorr(log10(as.matrix(data[cols])))
# Correlation of only True-positives
Hmisc::rcorr(
  log10(as.matrix(data[data$`Ground truth`=="True-positive", cols])))
# Correlation of only True-negatives
Hmisc::rcorr(
  log10(as.matrix(data[data$`Ground truth`=="True-negative", cols])))
# Correlation of only Unknowns
Hmisc::rcorr(log10(as.matrix(data[data$`Ground truth`=="Unknown", cols])))

rm(data, cols, fmt, i)
```

CAPTION: Scatter plot of the main tests Euroimmun S1 IgG vs Roche N IgG. The dashed lines indicate the manufacturer decision thresholds (1.1 for Euroimmun S1 IgG and 1.0 for Roche N IgG). Coloring by known true or negative cases. The R value indicates the Pearson correlation coefficient, with associated p-value. The numbers n indicate the number of cases in the respective quadrants.

## EI-S1-IgA vs -IgG (Excluded)

```{r, fig.width=5, fig.height=3.5}
data = extract_last_values(single_data)[c(columns$main, "Ground truth")]

for (i in 1:length(columns$main)) {
  colnames(data)[colnames(data)==columns$main[i]] = columns_pretty$main[i]
}

plt_iga_igg = ggplot(data, aes(x=`EI-S1-IgA`, y=`EI-S1-IgG`)) +
  geom_point(aes(col=`Ground truth`), alpha=0.5) +
  scale_x_log10() +scale_y_log10() +
  # Thresholds
  geom_vline(aes(xintercept = cutoff$old$Eur_IgA),
             linetype = style$thr_lt_old, color=style$thr_lc_old) +
  geom_vline(aes(xintercept = cutoff$new$Eur_IgA),
             linetype = style$thr_lt_new, color=style$thr_lc_new) +
  geom_hline(aes(yintercept = cutoff$old$Eur_IgG,
                 linetype = style$thr_lb_old), color=style$thr_lc_old) +
  geom_hline(aes(yintercept = cutoff$new$Eur_IgG,
                 linetype = style$thr_lb_new), color=style$thr_lc_new) +
  scale_linetype_manual(
    name="Cut-off", values=c(style$thr_lt_old,style$thr_lt_new)) +
  #geom_smooth(formula=y~x, method="lm") +
  ggpubr::stat_cor() +
  # geom_abline(linetype="dashed") +
  scale_fill_manual(values=style$pal3) + scale_color_manual(values=style$pal3)
plt_iga_igg

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("EuroimmunIgA_EuroimmunIgG_Scatter.", fmt)),
  #       device=fmt, dpi=style$dpi, width=5, height=3.5, units="in")
}

cols = c("EI-S1-IgA","EI-S1-IgG")
# Correlation of all (as in plot)
Hmisc::rcorr(log10(as.matrix(data[cols])))
# Correlation of only True-positives
Hmisc::rcorr(
  log10(as.matrix(data[data$`Ground truth`=="True-positive", cols])))
# Correlation of only True-negatives
Hmisc::rcorr(
  log10(as.matrix(data[data$`Ground truth`=="True-negative", cols])))
# Correlation of only Unknowns
Hmisc::rcorr(log10(as.matrix(data[data$`Ground truth`=="Unknown", cols])))

rm(data, cols, fmt, i)
```

## Qualitative comparison

```{r, fig.height=3.5, fig.width=5}
# Here we use the new cutoff only
cutoffs = cutoff$new

data = extract_last_values(single_data)
data[columns_pretty$eur_iga] = ifelse(
  data[columns$eur_iga] >= cutoffs$Eur_IgA, "Positive", "Negative")
data[columns_pretty$eur_igg] = ifelse(
  data[columns$eur_igg] >= cutoffs$Eur_IgG, "Positive", "Negative")
data[columns_pretty$roche] = ifelse(
  data[columns$roche] >= cutoffs$Roche, "Positive", "Negative")
data = data[columns_pretty$main]

# Create contingency matrices as data frame
contis = create_contingency_matrix(data)
# To long format
contis_long = reshape2::melt(contis, id.vars=c("Methods", "total"), 
                             value.name="Percentage")
colnames(contis_long)[colnames(contis_long) == 'variable'] = "Test outcomes"
contis_long$Methods = stringr::str_replace(contis_long$Methods, " & ", " \n& ")

plt_main_pairs = ggplot(contis_long,
                        aes(fill=`Test outcomes`, color=`Test outcomes`,
                            x=Methods, y=Percentage)) +
  # Stacked percentage bars
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  # Total numbers
  geom_text(data=contis_long[!duplicated(contis_long$Methods),],
            aes(x=Methods, y=1.05, label=total), color="black") +
  # y axis to percent
  scale_y_continuous(labels=scales::percent) +
  scale_fill_manual(values=style$pal4) +
  scale_color_manual(values=style$pal4) +
  labs(x="")
plt_main_pairs

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Main_Accordance.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6, height=3.5, units="in")
}

rm(data, contis, contis_long, fmt, cutoffs)
```

CAPTION: Qualitative agreement of the main tests. The manufacturer decision thresholds were used to decide whether a test is positive or negative.

# Qualitative concordance of tests and ground truth

TODO The following plot should probably be replaced by the subsequent one.

```{r, fig.width=16, fig.height=3.5}
data = to_numeric(extract_last_values(single_data))

rec = get_recovery_rates(data, columns$all, cutoff$new)
# Total number of cases with measurement and ground truth
rec$total = rec[,"n"] + rec[,"p"]

# To percent
val_cols = c("p_truepos", "n_truepos", "p_trueneg", "n_trueneg")
rec[,val_cols] = rec[,val_cols] / rec[,"total"]

# To long
rec_long = reshape2::melt(
  rec[,c("Method", "total", val_cols)],
  id.vars=c("Method", "total"), value.name="Percentage")
colnames(rec_long)[colnames(rec_long) == 'variable'] = "Outcomes"

# Prettify methods
cols_pretty = stringr::str_replace_all(
  columns_pretty$all, c("Euroimmun "="Euroimmun \n", "Roche "="Roche \n"))

rec_long$Method = as.character(rec_long$Method)
for (i in 1:length(columns$all)) {
  rec_long[rec_long==columns$all[i]] = cols_pretty[i]
}
# For correct order
rec_long$Method = factor(rec_long$Method, levels=cols_pretty)

# Prettifiy indicators
val_cols_pretty = c(
  "Test-positive - True-positive", "Test-negative - True-positive",
  "Test-positive - True-negative", "Test-negative - True-negative")
rec_long$Outcomes = as.character(rec_long$Outcomes)
for (i in 1:length(val_cols)) {
  rec_long[rec_long$Outcomes==val_cols[i] &
           !is.na(rec_long$Outcomes), "Outcomes"] = val_cols_pretty[i]
}
rec_long$Outcomes = factor(rec_long$Outcomes, levels=val_cols_pretty)

ggplot(rec_long, aes(fill=Outcomes, color=Outcomes, x=Method, y=Percentage)) + 
  geom_bar(position="fill", stat="identity", alpha=0.5) +
  theme(axis.text.x = element_text(angle=0, vjust=0.5)) +
  geom_text(data=rec_long[!duplicated(rec_long$Method),],
            aes(x=Method, y=1.05, label=total), color="black") +
  scale_fill_manual(values=style$pal4) + scale_color_manual(values=style$pal4)

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("All_GroundTruth_Accordance.", fmt)),
  #       device=fmt, dpi=style$dpi, width=26, height=3.5, units="in")
}

rm(rec, val_cols, rec_long, i, val_cols_pretty, cols_pretty, data, fmt)
```

Split up into true positives and true negatives:

```{r, fig.width=12, fig.height=2.5}
# Test indices of interest (sorry, not pretty)
ixs = c(1, 2, 5, 8, 11, 12, 13, 14)
cols = columns$confirmatory[ixs]
cols_pretty = columns_pretty$confirmatory[ixs]
plt_test_gt_bars_conf = test_gt_bars(
  single_data, cols, cols_pretty, 8, cutoff)
plt_test_gt_bars_conf

rm(ixs, cols, cols_pretty)
```

All confirmatory tests:

```{r, fig.width=12, fig.height=4}
cols = columns$confirmatory
cols_pretty = columns_pretty$confirmatory

# Remove the new cutoffs for VC-non-IgG
cutoff_tmp = new.env()
cutoff_tmp$old = cutoff$old
cutoff_tmp$new = cutoff$new
for (col in grep("(IgA|IgM)", columns$vc, value=T)) {
  cutoff_tmp$new[col] = NA
}

plt_test_gt_bars_conf_all =
  test_gt_bars(single_data, cols, cols_pretty, 7, cutoff_tmp)
plt_test_gt_bars_conf_all

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("GroundTruth_All_Split_Accordance.", fmt)),
  #       device=fmt, dpi=500, width=12, height=4, units="in")
}

rm(cols, cols_pretty, cutoff_tmp, col, fmt)
```

# Additional plots

## Number of positives for each test (Excluded)

```{r}
data = extract_last_values(single_data)
data = data[!is.na(data$cPass_result),]
methods_list = list(
  c("Eur_IgG_result"), c("Roche_result"), c("Eur_IgG_result", "Roche_result"),
  c("Eur_IgG_result", "Roche_result", "cPass_result"),
  c("Eur_IgG_result", "Roche_result", "NT_result"),
  c("Eur_IgG_result", "Roche_result", "cPass_result", "NT_result"))

data_long = data.frame(Methods=character(), Positive=double())
for (methods in methods_list) {
  print(methods)
  data$Positive = F
  for (method in methods) {
    print(method)
    data[is.na(data[,method]),"Positive"] = NA
    data$Positive = data$Positive | data[,method]=="Positive"
  }
  print(sum(data$Positive==T, na.rm=T))
  fraction = sum(data$Positive==T, na.rm=T) / sum(!is.na(data$Positive))
  data_long = data_long %>% tibble::add_row(
    Methods=paste(methods, collapse=" | "),
    Positive=fraction)
}

ggplot(data=data_long, aes(x=Methods, y=Positive)) + geom_col() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rm(data, data_long, methods, method, fraction)
```

## Parallel line plots (Spaghetti plots)

```{r, fig.width=9, fig.height=3.5}
cols = columns$vc
cols_pretty = columns_pretty$vc

# Remove the new cutoffs for VC-non-IgG
cutoff_tmp = new.env()
cutoff_tmp$old = cutoff$old
cutoff_tmp$new = cutoff$new
for (col in grep("(IgA|IgM)", cols, value=T)) {
  cutoff_tmp$new[col] = NA
}

plp_vc = spaghetti_with_discrete(
  single_data, cols, cols_pretty, "<10", 7, cutoff_tmp,
  c(7,10,30,100,300), c("<10","10","30","100","300"))
plp_vc

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Array_Spaghetti.", fmt)),
  #       device=fmt, dpi=style$dpi, width=9, height=3.5, units="in")
}

rm(cutoff_tmp, cols, cols_pretty, fmt)
```

Only IgG

```{r, fig.width=4.5, fig.height=3.5}
cols = grep("IgG", columns$vc, value=T)
cols_pretty = grep("IgG", columns_pretty$vc, value=T)

plp_vc_igg = spaghetti_with_discrete(
  single_data, cols, cols_pretty, "<10", 7, cutoff,
  c(7,10,30,100,300), c("<10","10","30","100","300"))
plp_vc_igg

rm(cols, cols_pretty)
```

```{r, fig.width=4.5, fig.height=3.5}
plp_lineblot = spaghetti_with_discrete(
  single_data, columns$lineblot, columns_pretty$lineblot,
  "not_reactive", 0.7, cutoff,
  c(0.7,1,3,10), c("<1", "1", "3","10"))
plp_lineblot
```

CAPTION: Parallel coordinate plot for the Array and the Line Blot tests. The lines connect values for the same sample. Coloring by known positive and negative cases.

```{r, fig.width=6, fig.height=4}
data = extract_last_values(single_data)

data_long = data %>% tidyr::gather(Array, Concentration, columns$main)
data_long$Concentration = as.numeric(data_long$Concentration)
# For plotting, we need the array IDs as numbers
for (i in 1:length(columns$main)) {
  data_long[data_long$Array==columns$main[i] &
            !is.na(data_long$Array),"Array_i"] = as.character(i)
}
# Cutoffs
for (col in columns$main) {
  data_long[data_long$Array==col,"Old_cutoff"] = cutoff$old[col]
  data_long[data_long$Array==col,"New_cutoff"] = cutoff$new[col]
}

plt_spaghetti_main = ggplot(data=data_long,
                            aes(y=Concentration, x=Array_i, group=tln_ID,
                                color=`Ground truth`)) +
  geom_line(alpha = 0.07) + geom_point(alpha = 0.5) +
  # Horizontal lines for decision thresholds
  geom_segment(data=data_long[!duplicated(data_long["Array_i"]),],
               color=style$thr_lc_old,
               aes(x=as.numeric(Array_i)-0.5, y=as.numeric(Old_cutoff),
                   xend=as.numeric(Array_i)+0.5, yend=as.numeric(Old_cutoff),
                   linetype=style$thr_lb_old)) +
  geom_segment(data=data_long[!duplicated(data_long["Array_i"]),],
               color=style$thr_lc_new,
               aes(x=as.numeric(Array_i)-0.5, y=as.numeric(New_cutoff),
                   xend=as.numeric(Array_i)+0.5, yend=as.numeric(New_cutoff),
                   linetype=style$thr_lb_new)) +
  scale_linetype_manual(
    name="Cut-off", values=c(style$thr_lt_old,style$thr_lt_new)) +
  # Decoration
  scale_x_discrete(labels=columns_pretty$main) + scale_y_log10() +
  scale_fill_manual(values=style$pal3) +
  scale_color_manual(values=style$pal3) +
  labs(x="", y="Measurement value")
plt_spaghetti_main

# Save plot
for (fmt in style$output_formats) {
  #ggsave(here_out(paste0("Main_Spaghetti.", fmt)),
  #       device=fmt, dpi=style$dpi, width=6, height=4, units="in")
}

rm(data, data_long, i, col, fmt)
```

# Final integrated figures

## Primary distributions (Figure 2 and Supplement)

```{r, fig.width=12, fig.height=3}
#plot_grid(
#  title_plot(
#    "A Distributions of primary tests",
#    plt_main_distr),
#  title_plot(
#    "B Reliability of the primary tests on multiple measurements",
#    plot_grid(plt_rep_bar, NULL, rel_widths=c(2,2.5))),
#  nrow=2)

plt_main_distr

for (fmt in style$output_formats) {
  ggsave(here_out(paste0("Fig_Primary_Distribution.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=3, units="in")
}
```

```{r, fig.width=6, fig.height=3}

plt_rep_bar

# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("FigSupp_Primary_Distribution.", fmt)), device=fmt,
         dpi=style$dpi, width=6, height=3, units="in")
}
```

## Primary comparison (Figure 4)

```{r, fig.width=12, fig.height=3}
load(here_r("Lab-Fig-6-Part-A.RData"))

#plot_grid(
#  plot_grid(
#    title_plot("A Performance comparison of primary tests",
#               plot_grid(iga.igg, roche.igg + theme(axis.title.y=element_blank()),
#                         nrow = 1, rel_widths = c(1.05,1))),
#    title_plot("B Parallel coordinate plot of primary tests", plt_spaghetti_main),
#    nrow=1, rel_widths = c(3,2.2)),
#  plot_grid(
#    title_plot("C Concordance of primary tests", plt_main_pairs),
#    title_plot("D Concordance of primary tests and ground truth", plt_main_gt_bar),
#    nrow=1, rel_widths = c(2,3)),
#  nrow=2
#)

plot_grid(
  title_plot("A Performance comparison of primary tests",
             plot_grid(iga.igg, roche.igg + theme(axis.title.y=element_blank()),
                       nrow = 1, rel_widths = c(1.05,1))),
  title_plot("B Parallel coordinate plot of primary tests", plt_spaghetti_main),
  nrow=1, rel_widths = c(3,2.2))

# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("Fig_Primary_Comparison.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=3, units="in")
}
```

```{r, fig.width=12, fig.height=3}
plot_grid(
  title_plot("A Concordance of primary tests", plt_main_pairs),
  title_plot("B Concordance of primary tests and ground truth", plt_main_gt_bar),
  nrow=1, rel_widths = c(2,3))

# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("2_Fig_Primary_Concordance.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=3, units="in")
}
```

## Confirmatory distribution and comparison (Figure 5)

```{r, fig.width=12, fig.height=6.5}
#plot_grid(
#  plot_grid(
#    title_plot("A Distribution of NT", plt_nt + theme(legend.position="none")),
#    title_plot("B Distribution of VC-IgG and MG", plot_grid(
#      plt_vc_distr_igg + theme(legend.position="none"),
#      plt_lineblot_distr + theme(legend.position="none", axis.title.y = element_blank()),
#      get_legend(plt_vc_distr_igg), rel_widths=c(2.18,2,1), nrow=1)),
#    rel_widths=c(4,11)),
#  plot_grid(
#    title_plot("C Distribution of GS-cPass", plt_cpass + theme(legend.position="none")),
#    title_plot("D Parallel coordinate plots for VC-IgG and MG", plot_grid(
#      plp_vc_igg + theme(legend.position="none"),
#      plp_lineblot + theme(legend.position="none", axis.title.y = element_blank()),
#      get_legend(plp_vc_igg), rel_widths=c(2.18,2,1), nrow=1)),
#    rel_widths=c(4,11)),
#  #title_plot("E Concordance of confirmatory tests and ground truth", plt_test_gt_bars_conf),
#  ncol=1,
#  #rel_heights = c(2,2,1.5)
#  rel_heights = c(2,2)
#)

library(patchwork)

plt_nt + theme(legend.position="none") + labs(tag='A') +
  plt_cpass + theme(legend.position="none", axis.title.y = element_blank()) +labs(tag='B') +
  plt_vc_distr_igg + theme(legend.position="none") + labs(tag='C') +
  plt_lineblot_distr + theme(legend.position="none", axis.title.y = element_blank()) +labs(tag='D') +
  get_legend(plt_cpass) +
  plot_layout(widths = c(2,2,0.8),
              heights = c(1,1,1,1),
              design = "AB#\nABE\nCDE\nCD#")


# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("Fig_Confirmatory_Distribution.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=6.5, units="in")
}
```

```{r, fig.width=7, fig.height=5}
plp_vc_igg


# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("2_Fig_VC_Spaghetti.", fmt)), device=fmt,
         dpi=style$dpi, width=7, height=5, units="in")
}
```

## Common Cold (Supplementary Figure 9)

```{r, fig.width=12, fig.height=3.5}
plot_grid(
  title_plot("A Distribution of Common Cold tests", plt_cold + theme(legend.position = "none")),
  title_plot("B Comparison of Common Cold tests and Ro-N-Ig", plt_cold_roche + theme(legend.position = "none")),
  get_legend(plt_cold), nrow=1, rel_widths=c(2.3,2,0.7))

# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("2_FigSupp_Cold.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=4, units="in")
}
```

## Main replicates (Supplementary Figure 1)

```{r, fig.height=7, fig.width=7}
cowplot::plot_grid(plt_rep_eur, plt_rep_roche, nrow=2, labels="AUTO")

# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("FigSupp_Replicates_Scatter.", fmt)), device=fmt,
         dpi=style$dpi, width=7, height=7, units="in")
}
```

## Full VC Array distribution and comparison (Supplementary Figure 4)

```{r, fig.width=12, fig.height=5}
#plot_grid(
#  title_plot("A Distribution of VC", plt_vc_distr),
#  title_plot("B Parallel coordinate plot of VC", plp_vc),
#  nrow=2
#)

plt_vc_distr
# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("FigSupp_VC.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=5, units="in")
}
```

```{r, fig.width=12, fig.height=5}
plp_vc
# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("2_FigSupp_VC_Spaghetti.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=5, units="in")
}
```

## Full Confirmatory Performances (Supplementary Figure 5)

```{r, fig.width=12, fig.height=4}
plt_test_gt_bars_conf_all

# Save plot
for (fmt in style$output_formats) {
  ggsave(here_out(paste0("FigSupp_GroundTruth_All_Split_Accordance.", fmt)), device=fmt,
         dpi=style$dpi, width=12, height=4, units="in")
}
```
